```{r setup and tests, include=FALSE}

## README FIRST ##
#Read and run this chunk of code line by line in the R Console (do not press knit) - there are some questions below which you will have to answer and some logic tests to complete. Once you are happy that the conditions have been satisfied, hit 'knit' above. 

#modified for TDN by Eric Jolin
#ejolin@alumni.uoguelph.ca

# Load required packages

library(leaflet)
library(dplyr)
library(colortools)
library(corrplot)
library(lubridate)
library(sf)
library(tmap)
library(stringr)
library(tidyr)
library(viridis)
###########NOTE: Need to find replacement for wheel function from colortools

# Load your data [change the files paths to your data locations]
# img - image data (including blank images)
# dat - detection data (img, but excluding blank images)
# eff - deployment data (effort)
# sta - station covariates
# ind - independent detection data
# tuyeta - shapefile outline of the study area
# spatdata - independent detections joined spatially with lat longs

project<-"TDN"
independent <- 30 # what threshold did you use (in minutes) for independent detections?

img <- read.csv("Processed_Data/TDN_CAM_Detection_Data_v7.csv", header=T)
img$species_rank<-as.factor(img$species_rank)
img$common_name<-as.factor(img$common_name)
summary(img$species_rank)
summary(img$common_name)
# drop detections that aren't ID-ed to at least the species level:
dat<-droplevels(img[img$species_rank %in% c("Species","Subspecies"),])


eff <- read.csv("Processed_Data/TDN_CAM_Deployment_Data_v7.csv", header=T)

sta <- read.csv("Raw_Data/TDN_Station_Covariates_v2.csv", header=T)
sta <- filter(sta, cam_data == T)
str(sta)

ind <- read.csv("Processed_Data/TDN_CAM_Independent_Detections_v7.csv", header=T)
str(ind)
unique(dat$common_name)
ind<-droplevels(ind[ind$common_name %in% unique(dat$common_name),])


TDN <- st_read("Spatial/TDN_Boundary/TDN_Boundary.shp")
TDN <- st_transform(TDN, crs = 3580)

spatdata=st_read("Raw_Data/TDN_Station_Covariates_v2.csv",
        options=c("X_POSSIBLE_NAMES=longitude","Y_POSSIBLE_NAMES=latitude"))

spatdata<- merge(spatdata, ind, by = "location")

spatdata$common_name<-as.factor(spatdata$common_name)
spatdata$location<-as.factor(spatdata$location)


# Timezone [Use UTC if your cameras do not correct for daylight saving time, if they do use the timezone where the data was collected]
tz <- "UTC"

# Set a single categorical variable of interest from station covariates for summary graphs. If you do not have an appropriate category use "Project.ID".
category <- "project"

# Define a colour from the R options to base the colourscheme
colour <- "lightseagreen"



## DATA TESTS ##


# This code will not work unless your data passes the following checks
 
# 2) All dates must be in YYYY-MM-DD in 'eff' and YYYY-MM-DD HH:MM:SS in 'dat' 
# If the following return NA, change your formatting
strptime(eff$deployment_begin_date[1], "%Y-%m-%d", tz="UTC")
strptime(dat$date_detected[1], "%Y-%m-%d %H:%M:%S", tz="UTC")

# 3) the dates in 'eff$deployment_end_date' must be the when the camera fails, not when you check the camera. If the camera fails (due to damage or full sd card), use the last day it functions here.  

# 4) Ensure your species names are consistent - check in the list below
table(dat$common_name)

# 5) Ensure Number.of.Animals doesn't have any non-numeric data in! The following should return TRUE
is.numeric(dat$count)

# 6) ensure all deployment dates are before retrieval dates for each deployment
# Logic = are the stations active for 0 or more days -> all should read TRUE
table((strptime(eff$deployment_end_date, "%Y-%m-%d", tz="UTC")-strptime(eff$deployment_begin_date, "%Y-%m-%d", tz="UTC"))>=0)

# 7) Do you have lat/long data for all of your sites you have effort data for? If yes, the value should be 0
length(setdiff(eff$location, sta$location))
# If length > 0, then you have some data missing!

# If all of the above is satisfied -> press 'Knit' above ^

```
#NOTE: Need to find replacement function for colortools
#NOTE: Need to figure out way to drop Humans

```{r non-adjustable options, echo=F, include=F}


# Prepare dates
eff$deployment_begin_date <- as.POSIXct(strptime(eff$deployment_begin_date, "%Y-%m-%d", tz ))
eff$deployment_end_date <- as.POSIXct(strptime(eff$deployment_end_date, "%Y-%m-%d", tz ))

eff$Days <- as.numeric(round(difftime(eff$deployment_end_date, eff$deployment_begin_date, units="days"),1))

dat$date_detected <- as.POSIXct(strptime(dat$date_detected, "%Y-%m-%d %H:%M:%S", tz ))

# Count the number of camera stations
n.stat <- length(unique(eff$location))
n.stat

# Generate colours to display the category levels - R needs them as a factor
sta$project <- as.factor(sta$project)
col.cat <- wheel(colour, num = length(levels(sta[,"project"])))
sta$Cols <- col.cat[sta[,"project"]]

# How big should the figures be
eff.height <- 8
if(length(unique(eff$location))>80)
   {
     eff.height <- length(unique(eff$location))/10
   }

sp.height <- 7
if(length(unique(dat$Species))>20)
   {
     sp.height <- 7+(length(unique(dat$Species))/8)
   }


```


# `r project` Project

### Camera locations

To date there have been camera deployments at `r n.stat` unique locations.

```{r map, echo=F}

m <- leaflet() %>%
  addProviderTiles(providers$Esri.WorldImagery, group="Satellite") %>%  # Add satellite data
  addProviderTiles(providers$Esri.WorldTopoMap, group="Base") %>%     
  addCircleMarkers(lng=sta$longitude, lat=sta$latitude,
                   color=sta$Cols,
                   popup=paste(sta$location, sta[,"project"])) %>%
 addLegend("bottomleft", colors = col.cat,  labels = levels(sta[,"project"]),
    title = category,
    labFormat = labelFormat(prefix = "$"),
    opacity = 1
  ) %>%
  # Layers control
  addLayersControl(
    baseGroups = c("Satellite", "Base"),
    options = layersControlOptions(collapsed = FALSE)
  )
m


```

### Camera activity through time

The `r n.stat` stations have resulted in a total of `r as.character(round(sum(eff$Days, na.rm=T),0))` camera days (mean = `r round(mean(aggregate(Days~location, data=eff,  FUN=sum, na.rm=T)$Days),1)` days per station; min = `r round(min(aggregate(Days~location, data=eff,  FUN=sum, na.rm=T)$Days),1)`; max = `r round(max(aggregate(Days~location, data=eff,  FUN=sum, na.rm=T)$Days),1)`).The daily break down of camera activity is as follows:

```{r activity, echo=F, fig.height=eff.height}

# Adjust layout
par(mar=c(2,6,1,1))
plot(c(min(eff$deployment_begin_date, na.rm=T), max(eff$deployment_end_date, na.rm=T)), c(1,n.stat), las=1, ylab="", xlab="", type="n", yaxt="n")

# Have the first station plot at the top 
plot.order <- rev(unique(eff$location))

axis(2, at= 1:n.stat, labels= plot.order, las=1, cex.axis=0.4)
#mtext("Camera Deployment ID", 2, 4)
# Make lines for each of the cameras
for(i in 1:length(plot.order))
{
  abline(h=i, col=rgb(0,0,0,0.1))
  tmp <- eff[eff$location==plot.order[i],]
  for(j in 1:nrow(tmp))
    {
      lines(c(tmp$deployment_begin_date[j],
                       tmp$deployment_end_date[j]),
            c(i,i), lwd=2)
    }
  
}

```

Figure 2: Where black lines denote a camera which is active, white space indicates cameras which are inactive.

####NOTE: BMS-SLU-033-07 still contains FOV errors (need to look at raw data for missing timelapse photos), but majority of sites are displaying correctly now.
#####UPDATE: BMS-SLU-033-07 raw data looked fine so deleted off wildtrax. Need to fix and reupload.

####Outliers
One outlier at BMS-CRU-004-01 is incorrect

## Raw camera detections

To date, there have been `r nrow(img)` image classifications, `r nrow(dat)` of which are classified as containing identified species (`r round((nrow(dat)/nrow(img))*100,1)`%).

Of the detections which have been identified, there are `r length(levels(factor(dat$common_name)))` species.

```{r captures, echo=F, fig.height=sp.height}
layout(matrix(c(1,1,2), 1, 3, byrow = TRUE))
det.sum.total <- as.data.frame(count(dat, common_name))
det.sum.total <- det.sum.total[order(det.sum.total$n),]

par(mar=c(5,16,1,1))
barplot(det.sum.total$n, names.arg = paste0(det.sum.total$common_name, 
                                           " (n =", det.sum.total$n,")")   , las=1, cex.names=1, xlab="Total raw detections", horiz=T)
i <-1
for(i in 1:nrow(det.sum.total))
{
  tmp <- subset(dat, common_name==det.sum.total$common_name[i])
  det.sum.total$Locations[i] <- length(unique(tmp$location))
}
par(mar=c(5,1,1,1))

barplot(det.sum.total$Locations/n.stat, las=1, cex.names=0.7, xlab="Proportion of stations detected", horiz=T, xlim=c(0,1))
abline(v=1, lty=2)

```

## Detection check

The following plot helps you determine if you have detections occurring outside of the times cameras are active. *Important note* You can still get detections outside of the activity period if you have decided that the field of view was shifted and the data is un-comparable to that which was collected earlier.

```{r, include=F}
# Make species colour codes
tmp3 <- data.frame("common_name"=unique(dat$common_name),"Colour"= wheel("lightseagreen", num = length(unique(dat$common_name))))

```

```{r detecion summary, echo=F, message=F, warning=F}

# To do this make a plot dataframe
tmp4 <- data.frame("location"=plot.order, "Plot.grp"=ceiling(1:length(unique(eff$location))/20))

eff <- left_join(eff,tmp4, by="location")

j <- 1
i <- 1
for(j in 1:length(unique(eff$Plot.grp)))
{
    layout(matrix(c(1,1,1,2), 1, 4, byrow = TRUE))
    par(mar=c(2,8,1,1))
    
    plot(c(min(eff$deployment_begin_date, na.rm=T), max(eff$deployment_end_date, na.rm=T)),      c(1,length(unique(eff$location[eff$Plot.grp==j]))), las=1, ylab="", xlab="", type="n", yaxt="n")
    
    axis(2, at= 1:length(unique(eff$location[eff$Plot.grp==j])), labels= unique(eff$location[eff$Plot.grp==j]), las=1, cex.axis=1)
    # Make lines for each of the cameras
    for(i in 1:length(unique(eff$location[eff$Plot.grp==j])))
    {
      abline(h=i, col=rgb(0,0,0,0.1))
      tmp <- eff[eff$location==unique(eff$location[eff$Plot.grp==j])[i],]
      
      tmp2 <- dat[dat$location==tmp$location[1],]
      tmp2 <- left_join(tmp2, tmp3)
      points(tmp2$date_detected, rep(i,nrow(tmp2)), pch="|", col= tmp2$Colour)
    
      for(k in 1:nrow(tmp))
        {
          lines(c(tmp$deployment_begin_date[k],
                           tmp$deployment_end_date[k]),
                c(i,i), lwd=2)
        }
      }
    par(mar=c(0,0,1,0))
    plot.new()
    legend("topleft", legend=tmp3$common_name, fill=tmp3$Colour, xpd=TRUE, cex=1.1 )

}

```

## Independent Detections

Using an independance threshold of `r independent` minutes, the number of detections is reduced to `r nrow(ind)`. The rest of the analyses are conducted with this data. The summary of detections is as follows:

```{r ind captures, echo=F, fig.height=sp.height, eval=T}

layout(matrix(c(1,1,2), 1, 3, byrow = TRUE))
det.sum.total <- as.data.frame(count(ind, common_name))
det.sum.total <- det.sum.total[order(det.sum.total$n),]

par(mar=c(5,16,1,1))
barplot(det.sum.total$n, names.arg = paste0(det.sum.total$common_name,
                                           " (n =", det.sum.total$n,")"), las=1, cex.names=1, xlab="Total independent detections", horiz=T)
i <-1
for(i in 1:nrow(det.sum.total))
{
  tmp <- subset(ind, common_name==det.sum.total$common_name[i])
  det.sum.total$Locations[i] <- length(unique(tmp$location))
}
par(mar=c(5,1,1,1))

barplot(det.sum.total$Locations/n.stat, las=1, cex.names=0.7, xlab="Proportion of stations detected", horiz=T, xlim=c(0,1))
abline(v=1, lty=2)

```

## Species metadata

Of the images classified as containing animals, the proportion of photographs assigned to the following catagories are as follows:

### Sex

```{r sex, echo=F, include=F}


b<-ind %>% group_by(common_name, sex) %>% summarise(n = sum(group_count))
d<-t(spread(b, sex, n))
e<-as.data.frame(d[2:4,])
names(e)<-d[1,]
e[is.na(e)]<-0
e
str(e)

tmp <- e
for (i in 1: ncol(e)){
  tmp[,i] <- as.numeric(e[,i])
}



dat[,"sex"] <- factor(dat[,"sex"])
cols <- wheel("lightseagreen", num = length(levels(dat[,"sex"])))

data_percentage <- apply(tmp, 2, function(x){x*100/sum(x,na.rm=T)})

```

```{r sex plot, echo=F, fig.height=sp.height}
layout(matrix(c(1,1,1,2), 1, 4, byrow = TRUE))
par(mar=c(5,10,1,1))
barplot(data_percentage , border="white",col= cols, ylab="", las=1, xlab="% of observations", cex.names=0.7, horiz=2)
par(mar=c(0,0,4,0))
plot.new()
legend("topleft", legend=row.names(tmp), fill=cols, xpd=TRUE, cex=1.1 )
```

### Age

```{r age, echo=F, include=F}

str(ind)

b<-ind %>% group_by(common_name, age_class) %>% summarise(n = sum(group_count))
d<-t(spread(b, age_class, n))
e<-as.data.frame(d[2:4,])
names(e)<-d[1,]
e[is.na(e)]<-0
e
str(e)

tmp <- e
for (i in 1: ncol(e)){
  tmp[,i] <- as.numeric(e[,i])
}


dat[,"age_class"] <- factor(dat[,"age_class"])
cols <- wheel("lightseagreen", num = length(levels(dat[,"age_class"])))


data_percentage <- apply(tmp, 2, function(x){x*100/sum(x,na.rm=T)})

```

```{r age plot, echo=F, fig.height=sp.height}
layout(matrix(c(1,1,1,2), 1, 4, byrow = TRUE))
par(mar=c(5,10,1,1))
barplot(data_percentage , border="white",col= cols, ylab="", las=1, xlab="% of observations", cex.names=0.7, horiz=2)
par(mar=c(0,0,4,0))
plot.new()
legend("topleft", legend=row.names(tmp), fill=cols, xpd=TRUE, cex=1.1 )

```

## Group size distribution

```{r group size, echo=F, eval=T,fig.height=sp.height}

ind2<-ind %>%
  group_by(event_id, common_name) %>%
  summarise(gc = sum(group_count))


par(mfrow=c(1,1))
par(mar=c(5,10,1,1))
plot(jitter(as.numeric(as.factor(ind2$common_name)))~jitter(as.numeric(ind2$gc)), xlab="Minimum group size", yaxt="n", las=1, ylab="")
axis(2, 1:length(unique(ind2$common_name)), labels=levels(as.factor(ind2$common_name)), las=2, cex.axis=0.6)

```

# Station-level species covariance

This plot shows the covariance between different species at the station level for species with \>5 unique detections. For example, if you typically get lots of caribou and bears at the same station, they will have positive covariance. If you get caribou where you don't get bears, they will have negative covariance.

```{r covariance, echo=F, fig.height=sp.height,fig.width=sp.height, eval=T}
par(mfrow=c(1,1))
tmp <- as.data.frame.matrix(table(ind$location, ind$common_name))
tmp <- tmp[colSums(tmp)>5]
M <- cor(tmp)

corrplot(M, method="color", #col=matrix(col(200)),
         type="upper", order="hclust",
         # addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=45, tl.cex = 0.7, #Text label color and rotation
         # Combine with significance
         # p.mat = p.mat, sig.level = 0.01, insig = "blank",
         # hide correlation coefficient on the principal diagonal
         diag=FALSE
         )

```

## Station-level temporal plots

### Summary

####NOTE: How can I change to monthly detection rates?

Across all sites and species:

```{r calculate monthly data summaries, echo=F, eval=T, include= F}
# Capture rates through time
focal.sp <- as.character(det.sum.total[det.sum.total$n>10,]$common_name)
focal.sp <- focal.sp[order(focal.sp)]
# Remove any blanks
focal.sp <- focal.sp[focal.sp!=""]

# We need to know how many detections there are in each month -> create a row lookup
# This is just a list of every day a camera was active.

tmp <- eff[is.na(eff$deployment_end_date)==F,]
daily.lookup <- list()
for(i in 1:nrow(tmp))
{
  if(as.Date(tmp$deployment_begin_date[i])!=as.Date(tmp$deployment_end_date[i]))
  {
    daily.lookup[[i]] <- data.frame("Date"=seq(as.Date(tmp$deployment_begin_date[i])+1, as.Date(tmp$deployment_end_date[i]), by="days"), "location"=tmp$location[i])
  }
}
row.lookup <- do.call(rbind, daily.lookup)

# Now determine capture rates
# Make a data frame by month and year
mon.dat <- unique(substr(ind$date_detected, 1,7))
mon.dat <- data.frame("Month"=mon.dat[order(mon.dat)], "Effort"= NA)
mon.dat[as.character(focal.sp)] <- NA
i<-1
for(i in 1:nrow(mon.dat))
{
  mon.dat$Effort[i] <- nrow(subset(row.lookup, substr(row.lookup$Date,1,7)==mon.dat$Month[i]))
  mon.dat$Total.CR[i] <- (nrow(subset(ind, substr(ind$date_detected,1,7)==mon.dat$Month[i]))/mon.dat$Effort[i])*100
}

for(i in 1:length(focal.sp))
{
  for(j in 1:nrow(mon.dat))
  {
    tmp <- subset(ind, common_name==as.character(focal.sp)[i] & substr(ind$date_detected,1,7)==mon.dat$Month[j])
    mon.dat[j, as.character(focal.sp[i])] <- (nrow(tmp)/mon.dat$Effort[j])*100
  }
}

mon.dat$timestamp <- strptime(paste0(as.character(mon.dat$Month),"-15"), "%Y-%m-%d")

# Remove any silly values 
mon.dat <- mon.dat[is.infinite(mon.dat$Total.CR)==F,]

```

```{r overall CR, echo=F, fig.height=4, eval=T}

par(mfrow=c(1,2))

xtick <- as.POSIXct(paste0(year(mon.dat$timestamp), "-", str_pad(month(mon.dat$timestamp), 2, side = "left", pad = "0"), "-01" ))



plot(mon.dat$timestamp, mon.dat$Effort, ylab="Monthly Effort (days)", xlab="Date", type="l", las=2)
points(mon.dat$timestamp, mon.dat$Effort, pch=19, col=rgb(0,0,0,0.4))
axis(side=1, at=xtick, labels = FALSE)

# Overall capture rate
plot(mon.dat$timestamp, mon.dat$Total.CR, ylab="Monthly Capture Rate", xlab="Date", type="l", las=2, ylim=c(0, max(mon.dat$Total.CR)))
points(mon.dat$timestamp, mon.dat$Total.CR, pch=19, col=rgb(0,0,0,0.4))
axis(side=1, at=xtick, labels = FALSE)

```



### Species-specific temporal trends

####NOTE: How can I change to monthly detection rates?

Species level variation in monthly capture rates, across all years, are as follows:

```{r, echo=F, eval=T}
par(mfrow=c(2,3))
for(i in 1:length(focal.sp))
{
  plot(mon.dat$timestamp, mon.dat[,as.character(focal.sp)[i]], ylab="Monthly Capture Rate", xlab="", type="l", las=2, main=focal.sp[i])
  points(mon.dat$timestamp, mon.dat[,as.character(focal.sp)[i]], pch=19, col=rgb(0,0,0,0.4))
  axis(side=1, at=xtick, labels = FALSE )
}

```

### Species-specific temporal trends, grouped by month

####NOTE: This is pooled monthly data but since we only have a small amount of monthly overlap, it would be better if the x-axis was just a calendar

Species level variation in monthly capture rates, with months of all years pooled, are as follows:

```{r make it a barplot instead and group months, echo = F}
par(mfrow=c(2,3))

monthly <- mon.dat %>% mutate(across(`American Robin`:`Wolverine`, ~.x *Effort/100),
                   month = month.abb[as.numeric(str_sub(Month, 6:6))]) %>%
  group_by(month) %>%
  summarise(effort = sum(Effort), across(`American Robin`:`Wolverine`, ~sum(.x))) %>%
  mutate(across(`American Robin`:`Wolverine`, ~.x / effort * 100))

monthly$month <- factor(monthly$month, levels = c("Jan","Feb","Mar","Apr","May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

monthly<-as.data.frame(monthly)

barplot(monthly$effort~monthly$month, par(las=2), ylab = "Effort (days)", xlab = "Month", main = "Overall Effort")

for ( i in 1: length(focal.sp)){
  barplot(monthly[,i+2] ~ monthly$month, par(las=2), ylab = "Capture Rate per 100 days", xlab = "Month", main = focal.sp[i])
}


```

## Species-specific maps

Gray circles are stations where there are no detections of that species. Blue circles are stations where that species was detected. The size of the circle increases with the number of independent detections, including group size.

###NOTE: I want to do this but without group size for the time being

###NOTE: in spatdata, the group_count column is currently filled with the FOV tag (i.e. within, out of range, etc). Need to fix this. Temporary solution, change group_count to gc_tag in script below which corresponds to count of animals in an individual tag not the actual group count. The maps produced by this temporary script are a bit wacky (very large circles for caribou herds). Multiple circles overlap when more than one camera at a site had detections.

```{r, eval=T, echo=F, message=FALSE, warning=FALSE}

# get rid of NA counts because they F up the script here
spatdata<-spatdata[!is.na(spatdata$gc_tag),]
species<-unique(spatdata$common_name)

i<-1

for (i in 1:length(species)){
  tmp<-spatdata[spatdata$common_name==species[i],]
  tmp2<-tmp%>%group_by(common_name, location) %>% summarise(n= sum(gc_tag))
  tmp2$n<-as.numeric(tmp2$n)
  
  x=tm_shape(TDN) +
    tm_borders() +
    tm_layout(
      title = species[i],
      title.position = c("center", "top"),
      inner.margins = c(0.07, 0.03, 0.15, 0.03)) +
    tm_shape(spatdata) +
    tm_symbols(size = 0.2, col="lightgrey") +
    tm_shape(tmp2) +
    tm_bubbles("n",
               col ='blue',
               breaks = c(1, 5, 10, max(tmp$n)),
               size.max = 10,
               sizes.legend= c(1, 5, 10, if(max(tmp2$n)>10) max(tmp2$n))) +
    tm_layout(legend.position = c("right","bottom"))
    
print(x)

}

```

#TEST TEST TEST
##CMI Workshop Scripts

###Site map - Basic
```{r}
m <- leaflet() %>%             # call leaflet
        addTiles() %>%         # add the default basemap
        addCircleMarkers(      # Add circles for stations
          lng=sta$longitude, lat=sta$latitude) 
m                              # return the map
```

###Site Map - Labels
```{r}
m <- leaflet() %>%             
        addTiles() %>%         
        addCircleMarkers(      
          lng=sta$longitude, lat=sta$latitude,
          popup=paste(sta$location)) # include a popup with the placename!
m                              
```

###Site Map - Labels+Sat
```{r}
m <- leaflet() %>%             
        addProviderTiles(providers$Esri.WorldImagery) %>% #Add Esri Wrold imagery         
        addCircleMarkers(      
          lng=sta$longitude, lat=sta$latitude,
          popup=paste(sta$location)) # include a popup with the placename!
m                              
```

###Site Map - ULTIMATE
```{r}
# First, set a single categorical variable of interest from station covariates for summary graphs. If you do not have an appropriate category use "project_id".
category <- "dom_habitat"

# We first convert this category to a factor with discrete levels
sta[,category] <- factor(sta[,category])
# then use the turbo() function to assign each level a color
col.cat <- turbo(length(levels(sta[,category])))
# then we apply it to the dataframe
sta$colours <- col.cat[sta[,category]]

m <- leaflet() %>%
  addProviderTiles(providers$Esri.WorldImagery, group="Satellite") %>%  
  addTiles(group="Base") %>%     # Include a basemap option too
  addCircleMarkers(lng=sta$longitude, lat=sta$latitude,
                   # Co lour the markers depending on the 'habitat type'
                   color=sta$colours,
                   # Add a popup of the placename and feature_type together 
                   popup=paste(sta$location, sta[,category])) %>%
  
  # Add a legend explaining what is going on
  addLegend("topleft", colors = col.cat,  labels = levels(sta[,category]),
                   title = category,
                   labFormat = labelFormat(prefix = "$"),
                   opacity = 1) %>%
  
  # add a layer control box to toggle between the layers
  addLayersControl(
                    baseGroups = c("Satellite", "Base"))

m
```

###Check for duplicate stations
```{r}
# create a list of all the non-duplicated placenames
camera_locs <- sta %>% 
  dplyr::select(location, latitude, longitude) %>% 
  unique() %>% # remove duplicated rows (rows where the placename and coordinates match)
  st_as_sf(coords = c("longitude", "latitude"), crs = "+proj=longlat") # Convert to `sf` format

# Check that there are no duplicated stations
camera_locs[duplicated(camera_locs$placename)==T,]
```


###Distance between cameras

####NOTE: figure out way to edit script to check distance between sites not cameras
```{r}
# distance matrix for all cameras
camera_dist <- st_distance(camera_locs) %>% 
                  as.dist() %>% 
                  usedist::dist_setNames(as.character(camera_locs$location)) %>% 
                  as.matrix()

# convert to pairwise list
camera_dist_list <- t(combn(colnames(camera_dist), 2))
camera_dist_list <- data.frame(camera_dist_list, dist = camera_dist[camera_dist_list]) %>% 
                          arrange(dist) # sort descending

# Duplicate and flip the stations so each one is represented on the left hand side
camera_dist_list <- rbind(camera_dist_list, camera_dist_list[,c(2,1,3)])

# keep just the closest camera for each location
camera_dist_list <- camera_dist_list %>% 
                  group_by(X1) %>% 
                  slice(which.min(dist))
summary(camera_dist_list$dist)
```
Most cameras average ~300m from nearest camera. Min distance between cameras is only 27.02m, find out which cameras these are:

BIO-TDN-032-02A : BIO-TDN-032-02B
27.01558

BIO-TDN-032-03A : BIO-TDN-032-03B
43.79968

BIO-TDN-021-04 : BIO-TDN-021-7NR
48.64840

BIO-TDN-032-01A : BIO-TDN-032-01B
99.20785

###Plotly map
```{r}
library(plotly)
fig <- plot_ly(data = sta,                    # Specify your data frame
               x = ~longitude, y = ~latitude, # The x and y axis columns
               type="scatter")                # and the type of plot
fig
```

```{r}
library(plotly)
fig <- plot_ly(data = sta,                    
               x = ~longitude, y = ~latitude,
               color=~angle_iron,              # We can specify color categories by angle iron
               type="scatter",
               marker=list(size=15))             # the default size is 10           
fig
```

###Plotly camera activity figure

```{r}
# Call the plot
p <- plot_ly()

# We want a separate row for each 'placename' - so lets turn it into a factor
eff$location <- as.factor(eff$location)

# loop through each place name
for(i in seq_along(levels(eff$location)))
  {
      #Subset the data to just that placename
      tmp <- eff[eff$location==levels(eff$location)[i],]
      # Order by date
      tmp <- tmp[order(tmp$deployment_begin_date),]
      # Loop through each deployment at that placename
      for(j in 1:nrow(tmp))
      {
        # Add a line to 'p'
        p <- add_trace(p, 
                       #Use the start and end date as x coordinates
                       x = c(tmp$deployment_begin_date[j], tmp$deployment_end_date[j]), 
                       #Use the counter for the y coordinates
                       y = c(i,i), 
                       # State the type of chart
                       type="scatter",
                       # make a line that also has points
                       mode = "lines+markers", 
                       # Add the deployment ID as hover text
                       hovertext=tmp$deployment_id[j], 
                       # Color it all black
                       color=I("black"), 
                       # Suppress the legend
                       showlegend = FALSE)
      }
      
  }
# Add a categorical y axis
 p <- p %>%   layout(yaxis = list(

      ticktext = as.list(levels(eff$location)), 

      tickvals = as.list(1:length(levels(eff$location))),

      tickmode = "array"))


p
```

####Outliers
One outlier at BMS-CRU-004-01 is incorrect.

```{r}
# Use to correct outlier after BMS-SLU-033-07 is fixed. Need to look at eff and change deployment_id

#eff$deployment_begin_date[eff$deployment_id=="d896"] <- ymd("2021-08-27") 
                                    #remember to format it as a date object
```

### Detection Check

Use img or dat dataframe? dat excludes tags not ID'd to species level

```{r}
# Make a separate plot for each 20 stations For each 20 stations
# To do this make a plot dataframe
tmp <- data.frame("deployment_id"=unique(eff$deployment_id), "plot_group"=ceiling(1:length(unique(eff$deployment_id))/305))

dep_tmp <- left_join(eff,tmp, by="deployment_id")

for(i in 1:max(dep_tmp$plot_group))
{  
  # Call the plot
  p <- plot_ly() 
  
  #Subset the data to just that placename
  tmp <- dep_tmp[dep_tmp$plot_group==i,]
  # Order by placename 
  tmp <- tmp[order(tmp$location),]
  
 
 # Loop through each deployment at that placename
  for(j in 1:nrow(tmp))
    {
        #Subset the image data
        tmp_img <- img[img$deployment_id==tmp$deployment_id[j],]
        
        if(nrow(tmp_img)>0)
        {
         
          p <- add_trace(p, 
                       #Use the start and end date as x coordinates
                       x = c(tmp_img$timestamp), 
                       #Use the counter for the y coordinates
                       y = rep(j, nrow(tmp_img)), 
                       # State the type of chart
                       type="scatter",
                       # make a line that also has points
                       mode = "markers", 
                       # Add the deployment ID as hover text
                       hovertext=paste(tmp_img$scientific_name,tmp_img$common_name), 
                       # Color it all black
                       marker = list(color = "red"), 
                       # Suppress the legend
                       showlegend = FALSE)
        }
        
       # Add a line to 'p'
        p <- add_trace(p, 
                       #Use the start and end date as x coordinates
                       x = c(tmp$deployment_begin_date[j], tmp$deployment_end_date[j]), 
                       #Use the counter for the y coordinates
                       y = c(j,j), 
                       # State the type of chart
                       type="scatter",
                       # make a line that also has points
                       mode = "lines", 
                       # Add the deployment ID as hover text
                       hovertext=tmp$deployment_id[j], 
                       # Color it all black
                       color=I("black"), 
                       # Suppress the legend
                       showlegend = FALSE)
      }
  # Add custom y axis labels  
  p <- p %>%   layout(yaxis = list(

      ticktext = as.list(tmp$deployment_id), 

      tickvals = as.list(1:nrow(tmp)),

      tickmode = "array"))
  
  print(p)
      
  
} 
```
Similar problem where only about 2/3 are input correctly. Also, showing detections per deployment doesn't really make much sense to me. I think showing detection by location would make much more sense. 

###Diel activity check 

Need to rework this code to work with img$date_detected OR need to split up img$date_detected into date:hours:minutes:seconds

Use img or dat dataframe? dat excludes tags not ID'd to species level

```{r}
# First lets convert our timestamp to decimal hours
img$hours <- hour(img$timestamp) + minute(img$timestamp)/60 + second(img$timestamp)/(60*60)

# Count all of the captures
tmp <- img %>% group_by(common_name) %>% summarize(count=n())

yform <- list(categoryorder = "array",
              categoryarray = tmp$common_name)

fig <- plot_ly(x = img$hours, y = img$common_name,type="scatter",
               height=1000, text=img$deployment_id, hoverinfo='text',
               mode   = 'markers',
               marker = list(size = 5,
                             color = 'rgba(50, 100, 255, .2)',
                             line = list(color = 'rgba(0, 0, 0, 0)',
                                         width = 0))) %>% 
              layout(yaxis = yform)
fig
```




