---
title: "GLMM_AllSpatialScales_Weekly_Cleaned"
output: html_document
date: "2024-04-05"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# README

Pared down script for only the final models used in analyses.  

For full list of models tested (e.g. previous ideas, global models, etc), look at 9d_GLMM_AllSpatialScales_Weekly_Cleaned.Rmd

This script is used to run GLMM analyses for each ecological process (top down, bottom up, apparent competition) and compete using AIC. Committee models are what I ended up using for the thesis.

This script also:
- tests overdispersion of models to justify use of NBD over poisson
- runs other GLMMs which include only single covariates, groups of covariates (e.g. topography), previous outdated ideas, global models, etc.
- Tests VIF across covariates included in models
- Some simple summary statistics to include in early parts of the results section. 


# Load the required packages

```{r}
# Check you have them and load them
list.of.packages <- c("kableExtra", "tidyr", "ggplot2", "gridExtra", "dplyr", "Hmsc", "jtools", "lubridate", "corrplot", "MuMIn","stringr","sf","raster","leaflet", "tidyverse","htmlwidgets","webshot", "purrr", "magick","forcats","multcomp", "reshape2", "lme4", "tidyr", "TMB", "glmmTMB", "car", "DHARMa")

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
lapply(list.of.packages, require, character.only = TRUE)
```

Landcovers are proportions and therefore don't need to be scaled as they are already between 1 and 0. topography and non-response variable species detections still need to be scaled. 

# 1. Region, Multiseason detections
```{r}
# Import the weekly regional multiseason dataset created in 9c_GLMM_Create_Datasets
mod_dat_wk <- read.csv("Processed_Data/glmm_wk_region_multi.csv", header=T)

#reorder factor levels for categorical variables
mod_dat_wk$target_cons <- fct_relevel(mod_dat_wk$target_cons, "None")
mod_dat_wk$target_hydro <- fct_relevel(mod_dat_wk$target_hydro, "None")
mod_dat_wk$target_linear <- fct_relevel(mod_dat_wk$target_linear, "None")

#check levels
levels(mod_dat_wk$target_cons)
levels(mod_dat_wk$target_hydro)
levels(mod_dat_wk$target_linear)
```

##VIF testing

Conducting VIF testing as multicollinearity seems to be a model issue when including all proportional landcovers. 

The smallest possible value of VIF is one (absence of multicollinearity). As a rule of thumb, a VIF value that exceeds 5 or 10 indicates a problematic amount of collinearity (James et al. 2014). 

Removing the dominant landcover (SPPSLM) brings VIF down to about 1 for other landcovers in every single seasonal and spatial data set.

```{r}
#model with SPPSLM (highest proportion of landcovers at both spatial extents) removed
model1<- glm(Caribou ~ z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPG + z.X300_TSPS + z.X300_BAR, data=mod_dat_wk, family = "poisson")

vif(model1)

#model with SPPSLM 
model2<- glm(Caribou ~ z.X300_SPPSLM + z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPG + z.X300_TSPS + z.X300_BAR, data=mod_dat_wk, family = "poisson")

vif(model2)
```

##Simple Models
let's run a couple super simple models, one with a random effect and one with the survey effort offset and no extra covariates:
```{r}
# GLMM with only a random effect
glmm_wk_random <- glmmTMB(Caribou ~ 1 + (1 | location_site), data = mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_random)

#GLMM with random and survey effort

glmm_wk_random_eff <- glmmTMB(Caribou ~ 1 +  offset(log(n_days_effort)) + (1 | location_site) , data = mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_random_eff)
```


```{r}
#GLMM with random, survey effort, snow season
glmm_wk_snowssn <- glmmTMB(Caribou ~ 1 + snow_season + offset(log(n_days_effort)) + (1 | location_site) , data = mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_snowssn)

#GLMM with random, survey effort, four season
glmm_wk_fourssn <- glmmTMB(Caribou ~ 1 + four_season + offset(log(n_days_effort)) + (1 | location_site) , data = mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_fourssn)

#GLMM with random, survey effort, week.
glmm_wk_wk <- glmmTMB(Caribou ~ 1 + week + offset(log(n_days_effort)) + (1 | location_site) , data = mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_wk)
```

## Target
```{r}
glmm_wk_tgt <- glmmTMB(Caribou ~ 
                     target_cons + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_tgt)

glmm_wk_tgt_h <- glmmTMB(Caribou ~ 
                     target_hydro  + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_tgt_h)

glmm_wk_tgt_l <- glmmTMB(Caribou ~ 
                     target_linear  + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_tgt_l)
```

## Committee Models

#### Bottom Up

#####NOTE: Completely misinterepreted model outputs for the bottom up models. Can't include every landcover because they're proportions and essentially add up to 1 (very high multicollinearity). The intercept essentially rperesents the model if the landcovers not included were set to one (i.e. a buffer of 100% the landcovers not inclded in the model) and the effects of the landcovers in the model are being compared against this. The direction (+/-) remains the same but the exponential of the estimate is used to show magnitude of effect (e.g. if the exp(estimate) of the BAR landclass is 0.9, then there is a 10% decrease in caribou detections relative to the omitted landcovers which would be represented by 1.0).

Omitting SPPSLM as it is the dominant landcover type captured within buffer areas (as per previous VIF testing). 

At the regional scale I would expect very strong negative effects of taiga-type landcovers and weaker negative effects at the local scale. May see positive effects of other landcover types or small landcovers at the local scale. 

At the regional scale, SPTNF and TSPBDF account for under 1% of all the land captured within the buffered areas and were omitted as well to avoid rare effects. 

wout target
```{r}
glmm_wk_comm_bu <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_comm_bu)
```

wtarget
```{r}
glmm_wk_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_comm_bu_tgt)
```


#### Top Down

wout target
```{r}
glmm_wk_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_comm_td)
```

w target
```{r}
glmm_wk_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + target_hydro + target_linear  + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_comm_td_tgt)
```

####Apparent Competition

w target
```{r}
glmm_wk_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_comm_app_tgt)
```

wout target
```{r}
glmm_wk_comm_app <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_comm_app)
```

#####Simplified App Comp
two sets of different simplified models to try to solve convergence issues suggested by committee.

Species Only. Species detections scaled within model formula.
######NOTE: This results in model outputs exactly the same as the unscaled ung+pred model...

wout tgt
```{r}
glmm_wk_comm_app_2 <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_comm_app_2)
```

w tgt
```{r}
glmm_wk_comm_app_2_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_comm_app_2_tgt)
```

Consolidated and scaled Ungulates (moose+muskox) and Predators (Wolves+Griz) and an interaction term for Ung*Pred

wout tgt
```{r}
glmm_wk_comm_app_3 <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_comm_app_3)
```

w tgt
```{r}
glmm_wk_comm_app_3_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + target_hydro + target_linear + (1|location_site) , data=mod_dat_wk, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_comm_app_3_tgt)
```

###Committee Model Selection
```{r}
model.sel(glmm_wk_random_eff, glmm_wk_wk, glmm_wk_tgt, glmm_wk_tgt_h, glmm_wk_tgt_l, glmm_wk_comm_bu, glmm_wk_comm_td, glmm_wk_comm_app, glmm_wk_comm_bu_tgt, glmm_wk_comm_td_tgt, glmm_wk_comm_app_tgt, glmm_wk_comm_app_2, glmm_wk_comm_app_2_tgt, glmm_wk_comm_app_3, glmm_wk_comm_app_3_tgt)
```

###Over-dispersion Testing

Null Model
```{r}
# Poisson version of the random effects model
poisson_random_eff <- glmmTMB(Caribou ~ 1 + offset(log(n_days_effort)) + (1 | location_site), 
                              data = mod_dat_wk, 
                              family = "poisson")

# Dispersion ratio
dispersion_ratio <- deviance(poisson_random_eff) / df.residual(poisson_random_eff)
dispersion_ratio  # >1.5 suggests overdispersion

# DHARMa check
library(DHARMa)
sim_res <- simulateResiduals(fittedModel = poisson_random_eff)
testDispersion(sim_res)
```

Bottom Up
```{r}
# Poisson version of the Bottom-Up model
poisson_comm_bu <- glmmTMB(Caribou ~ z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                           z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + 
                           offset(log(n_days_effort)) + (1 | location_site), 
                           data = mod_dat_wk, 
                           family = "poisson")

# Dispersion ratio
dispersion_ratio_comm_bu <- deviance(poisson_comm_bu) / df.residual(poisson_comm_bu)
dispersion_ratio_comm_bu

# DHARMa check
sim_res_comm_bu <- simulateResiduals(fittedModel = poisson_comm_bu)
testDispersion(sim_res_comm_bu)

# Poisson version of the Bottom-Up model with target variables
poisson_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                  z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + 
                  z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_bu_tgt <- deviance(poisson_comm_bu_tgt) / df.residual(poisson_comm_bu_tgt)
dispersion_ratio_bu_tgt

sim_res_bu_tgt <- simulateResiduals(fittedModel = poisson_comm_bu_tgt)
testDispersion(sim_res_bu_tgt)
```

Top Down
```{r}
# Poisson version of the Top-Down model without target variables
poisson_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td <- deviance(poisson_comm_td) / df.residual(poisson_comm_td)
dispersion_ratio_td

sim_res_td <- simulateResiduals(fittedModel = poisson_comm_td)
testDispersion(sim_res_td)

# Poisson version of the Top-Down model with target variables
poisson_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td_tgt <- deviance(poisson_comm_td_tgt) / df.residual(poisson_comm_td_tgt)
dispersion_ratio_td_tgt

sim_res_td_tgt <- simulateResiduals(fittedModel = poisson_comm_td_tgt)
testDispersion(sim_res_td_tgt)

```

Apparent Competition
```{r}
# Poisson version of the Apparent Competition model without target variables
poisson_comm_app <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app <- deviance(poisson_comm_app) / df.residual(poisson_comm_app)
dispersion_ratio_app

sim_res_app <- simulateResiduals(fittedModel = poisson_comm_app)
testDispersion(sim_res_app)

# Poisson version of the Apparent Competition model with target variables
poisson_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app_tgt <- deviance(poisson_comm_app_tgt) / df.residual(poisson_comm_app_tgt)
dispersion_ratio_app_tgt

sim_res_app_tgt <- simulateResiduals(fittedModel = poisson_comm_app_tgt)
testDispersion(sim_res_app_tgt)

```

#### Poisson Model Selection
```{r}
model.sel(poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt)
```


#############################################################################################

## Model Selection

###Save Model Selection
```{r}
# Capture the model selection
#summary_output <- capture.output(model.sel(glmm_wk_random_eff, glmm_wk_wk, glmm_wk_comm_bu, glmm_wk_comm_td, glmm_wk_comm_bu_tgt, glmm_wk_comm_td_tgt, glmm_wk_comm_app_2, glmm_wk_comm_app_2_tgt, glmm_wk_comm_app_3, glmm_wk_comm_app_3_tgt))

# Save the model selection to a CSV file
#write.csv(summary_output, file = "Tables/region_multi_models_fnl.csv", row.names = FALSE)
```

###Save Top Model
```{r}
# Capture the summary output
#summary_output <- capture.output(summary(glmm_wk_wk))

# Save the summary data to a CSV file
#write.csv(summary_output, file = "Tables/region_multi_wk.csv.csv", row.names = FALSE)
```

############################################################################################################################################################################################################################

# 2. Region, Summer detection data

```{r}
# Import the weekly regional summer dataset created in 9c_GLMM_Create_Datasets
mod_dat_wk_summer <- read.csv("Processed_Data/glmm_wk_region_smr.csv", header=T)

#reorder factor levels for categorical variables
mod_dat_wk_summer$target_cons <- fct_relevel(mod_dat_wk_summer$target_cons, "None")
mod_dat_wk_summer$target_hydro <- fct_relevel(mod_dat_wk_summer$target_hydro, "None")
mod_dat_wk_summer$target_linear <- fct_relevel(mod_dat_wk_summer$target_linear, "None")

#check levels
levels(mod_dat_wk_summer$target_cons)
levels(mod_dat_wk_summer$target_hydro)
levels(mod_dat_wk_summer$target_linear)
```

##Simple Models
```{r}
#null model
glmm_wk_smr_null <- glmmTMB(Caribou ~ 
                     offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_summer, family="nbinom2", control=glmmTMBControl(parallel=5))
summary(glmm_wk_smr_null)

#week model
glmm_wk_smr_wk <- glmmTMB(Caribou ~ 
                     week + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_summer, family="nbinom2", control=glmmTMBControl(parallel=5))
summary(glmm_wk_smr_wk)
```

## Target
```{r}
glmm_wk_smr_tgt <- glmmTMB(Caribou ~ 
                     target_cons + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_summer, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_smr_tgt)

glmm_wk_smr_tgt_h <- glmmTMB(Caribou ~ 
                     target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_summer, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_smr_tgt_h)

glmm_wk_smr_tgt_l <- glmmTMB(Caribou ~ 
                     target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_summer, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_smr_tgt_l)
```

## Committee Models

#### Bottom Up

#####NOTE: Removed TSPS in summer due to very large standard errors. Checked VIF and very high. Removal resulted in normal values across remaining landcovers.

wo tgt
```{r}
glmm_wk_smr_comm_bu <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_smr_comm_bu)
```

w tgt
```{r}
glmm_wk_smr_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + target_linear + target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_smr_comm_bu_tgt)
```

#### Top Down
wo tgt
```{r}
glmm_wk_smr_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_smr_comm_td)
```

w tgt
```{r}
glmm_wk_smr_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + target_linear + target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_smr_comm_td_tgt)
```

####Apparent Competition
wo tgt
```{r}
glmm_wk_smr_comm_app <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_smr_comm_app)
```

w tgt
```{r}
glmm_wk_smr_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + target_linear + target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_smr_comm_app_tgt)
```

#####Simplified App Comp
two sets of different simplified models to try to solve convergence issues suggested by committee.

Species Only. Species detections scaled within model formula.
######NOTE: This results in model outputs exactly the same as the unscaled ung+pred model...

wout tgt
```{r}
glmm_wk_smr_comm_app_2 <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_smr_comm_app_2)
```

w tgt
```{r}
glmm_wk_smr_comm_app_2_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_smr_comm_app_2_tgt)
```

Consolidated and scaled Ungulates (moose+muskox) and Predators (Wolves+Griz) and an interaction term for Ung*Pred

wout tgt
```{r}
glmm_wk_smr_comm_app_3 <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_smr_comm_app_3)
```

w tgt
```{r}
glmm_wk_smr_comm_app_3_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + target_hydro + target_linear + (1|location_site) , data=mod_dat_wk_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_smr_comm_app_3_tgt)
```

####Committee Model Selection
```{r}
model.sel(glmm_wk_smr_wk, glmm_wk_smr_null, glmm_wk_smr_tgt_h, glmm_wk_smr_tgt_l, glmm_wk_smr_comm_bu, glmm_wk_smr_comm_td, glmm_wk_smr_comm_app, glmm_wk_smr_comm_bu_tgt, glmm_wk_smr_comm_td_tgt, glmm_wk_smr_comm_app_tgt, glmm_wk_smr_comm_app_2, glmm_wk_smr_comm_app_2_tgt, glmm_wk_smr_comm_app_3, glmm_wk_smr_comm_app_3_tgt)
```

###Over-dispersion Testing

Null Model
```{r}
# Poisson version of the random effects model
poisson_random_eff <- glmmTMB(Caribou ~ 1 + offset(log(n_days_effort)) + (1 | location_site), 
                              data = mod_dat_wk_summer, 
                              family = "poisson")

# Dispersion ratio
dispersion_ratio <- deviance(poisson_random_eff) / df.residual(poisson_random_eff)
dispersion_ratio  # >1.5 suggests overdispersion

# DHARMa check
library(DHARMa)
sim_res <- simulateResiduals(fittedModel = poisson_random_eff)
testDispersion(sim_res)
```

Bottom Up
```{r}
# Poisson version of the Bottom-Up model
poisson_comm_bu <- glmmTMB(Caribou ~ z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                           z.X300_MF + z.X300_TSPG + z.X300_BAR + 
                           offset(log(n_days_effort)) + (1 | location_site), 
                           data = mod_dat_wk_summer, 
                           family = "poisson")

# Dispersion ratio
dispersion_ratio_comm_bu <- deviance(poisson_comm_bu) / df.residual(poisson_comm_bu)
dispersion_ratio_comm_bu

# DHARMa check
sim_res_comm_bu <- simulateResiduals(fittedModel = poisson_comm_bu)
testDispersion(sim_res_comm_bu)

# Poisson version of the Bottom-Up model with target variables
poisson_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                  z.X300_MF + z.X300_TSPG + z.X300_BAR + 
                  z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_summer, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_bu_tgt <- deviance(poisson_comm_bu_tgt) / df.residual(poisson_comm_bu_tgt)
dispersion_ratio_bu_tgt

sim_res_bu_tgt <- simulateResiduals(fittedModel = poisson_comm_bu_tgt)
testDispersion(sim_res_bu_tgt)
```

Top Down
```{r}
# Poisson version of the Top-Down model without target variables
poisson_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_summer, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td <- deviance(poisson_comm_td) / df.residual(poisson_comm_td)
dispersion_ratio_td

sim_res_td <- simulateResiduals(fittedModel = poisson_comm_td)
testDispersion(sim_res_td)

# Poisson version of the Top-Down model with target variables
poisson_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_summer, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td_tgt <- deviance(poisson_comm_td_tgt) / df.residual(poisson_comm_td_tgt)
dispersion_ratio_td_tgt

sim_res_td_tgt <- simulateResiduals(fittedModel = poisson_comm_td_tgt)
testDispersion(sim_res_td_tgt)

```

Apparent Competition
```{r}
# Poisson version of the Apparent Competition model without target variables
poisson_comm_app <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_summer, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app <- deviance(poisson_comm_app) / df.residual(poisson_comm_app)
dispersion_ratio_app

sim_res_app <- simulateResiduals(fittedModel = poisson_comm_app)
testDispersion(sim_res_app)

# Poisson version of the Apparent Competition model with target variables
poisson_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_summer, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app_tgt <- deviance(poisson_comm_app_tgt) / df.residual(poisson_comm_app_tgt)
dispersion_ratio_app_tgt

sim_res_app_tgt <- simulateResiduals(fittedModel = poisson_comm_app_tgt)
testDispersion(sim_res_app_tgt)

```

#### Poisson Model Selection
```{r}
model.sel(poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt)
```

#############################################################################################

## Model Selection
```{r}
model.sel(glmm_wk_smr_null, glmm_wk_smr_wk, glmm_wk_smr_lcc_2, glmm_wk_smr_dem, glmm_wk_smr_tgt_h, glmm_wk_smr_tgt_l, glmm_wk_smr_ung, glmm_wk_smr_comm_bu, glmm_wk_smr_comm_td, glmm_wk_smr_comm_app, glmm_wk_smr_esker, glmm_wk_smr_comm_bu_tgt, glmm_wk_smr_comm_td_tgt, glmm_wk_smr_comm_app_tgt)
```

###Save Model Selection
```{r}
# Capture the model selection
#summary_output <- capture.output(model.sel(glmm_wk_smr_null, glmm_wk_smr_comm_bu, glmm_wk_smr_comm_td, glmm_wk_smr_comm_bu_tgt, glmm_wk_smr_comm_td_tgt, glmm_wk_smr_comm_app_2, glmm_wk_smr_comm_app_2_tgt, glmm_wk_smr_comm_app_3, glmm_wk_smr_comm_app_3_tgt))

# Save the model selection to a CSV file
#write.csv(summary_output, file = "Tables/region_smr_models_fnl.csv", row.names = FALSE)
```

###Save Top Model
```{r}
# Capture the summary output
#summary_output <- capture.output(summary(glmm_wk_smr_comm_bu_tgt))

# Save the summary data to a CSV file
#write.csv(summary_output, file = "Tables/region_smr_comm_bu_tgt.csv", row.names = FALSE)
```

############################################################################################################################################################################################################################

# 3. Region, Fall detection data

```{r}
# Create a new data frame for winter
mod_dat_wk_fall <- read.csv("Processed_Data/glmm_wk_region_fall.csv", header=T)

#reorder factor levels for categorical variables
mod_dat_wk_fall$target_cons <- fct_relevel(mod_dat_wk_fall$target_cons, "None")
mod_dat_wk_fall$target_hydro <- fct_relevel(mod_dat_wk_fall$target_hydro, "None")
mod_dat_wk_fall$target_linear <- fct_relevel(mod_dat_wk_fall$target_linear, "None")

#check levels
levels(mod_dat_wk_fall$target_cons)
levels(mod_dat_wk_fall$target_hydro)
levels(mod_dat_wk_fall$target_linear)
```

##Simple Models
```{r}
#null model
glmm_wk_fall_null <- glmmTMB(Caribou ~ 
                     offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_fall_null)

#week model
glmm_wk_fall_wk <- glmmTMB(Caribou ~ 
                     week + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_fall_wk)
```

## Target
```{r}
glmm_wk_fall_tgt <- glmmTMB(Caribou ~ 
                     target_cons + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_fall, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_fall_tgt)

glmm_wk_fall_tgt_h <- glmmTMB(Caribou ~ 
                     target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_fall, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_fall_tgt_h)

glmm_wk_fall_tgt_l <- glmmTMB(Caribou ~ 
                     target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_fall, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_fall_tgt_l)
```

## Committee Models

#### Bottom Up
wo target
```{r}
glmm_wk_fll_comm_bu <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_fll_comm_bu)
```

target
```{r}
glmm_wk_fll_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_fll_comm_bu_tgt)
```

#### Top Down
wo target
```{r}
glmm_wk_fll_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_fll_comm_td)
```

w target
```{r}
glmm_wk_fll_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + target_linear + target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_fll_comm_td_tgt)
```

####Apparent Competition
wo target
```{r}
glmm_wk_fll_comm_app <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_fll_comm_app)
```

w target
```{r}
glmm_wk_fll_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_fll_comm_app_tgt)
```

#####Simplified App Comp
two sets of different simplified models to try to solve convergence issues suggested by committee.

Species Only. Species detections scaled within model formula.
######NOTE: This results in model outputs exactly the same as the unscaled ung+pred model...

wout tgt
```{r}
glmm_wk_fall_comm_app_2 <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_fall_comm_app_2)
```

w tgt
```{r}
glmm_wk_fall_comm_app_2_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_fall_comm_app_2_tgt)
```

Consolidated and scaled Ungulates (moose+muskox) and Predators (Wolves+Griz) and an interaction term for Ung*Pred

wout tgt
```{r}
glmm_wk_fall_comm_app_3 <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_fall_comm_app_3)
```

w tgt
```{r}
glmm_wk_fall_comm_app_3_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + target_hydro + target_linear + (1|location_site) , data=mod_dat_wk_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_fall_comm_app_3_tgt)
```


####Committee Model Selection
```{r}
model.sel(glmm_wk_fall_wk, glmm_wk_fall_null, glmm_wk_fall_tgt_h, glmm_wk_fall_tgt_l, glmm_wk_fll_comm_bu, glmm_wk_fll_comm_td, glmm_wk_fll_comm_app, glmm_wk_fll_comm_bu_tgt, glmm_wk_fll_comm_td_tgt, glmm_wk_fll_comm_app_tgt, glmm_wk_fall_comm_app_2_tgt, glmm_wk_fall_comm_app_2, glmm_wk_fall_comm_app_3, glmm_wk_fall_comm_app_3_tgt)
```

##############################################################################

###Over-dispersion Testing

Null Model
```{r}
# Poisson version of the random effects model
poisson_random_eff <- glmmTMB(Caribou ~ 1 + offset(log(n_days_effort)) + (1 | location_site), 
                              data = mod_dat_wk_fall, 
                              family = "poisson")

# Dispersion ratio
dispersion_ratio <- deviance(poisson_random_eff) / df.residual(poisson_random_eff)
dispersion_ratio  # >1.5 suggests overdispersion

# DHARMa check
library(DHARMa)
sim_res <- simulateResiduals(fittedModel = poisson_random_eff)
testDispersion(sim_res)
```

Bottom Up
```{r}
# Poisson version of the Bottom-Up model
poisson_comm_bu <- glmmTMB(Caribou ~ z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                           z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + 
                           offset(log(n_days_effort)) + (1 | location_site), 
                           data = mod_dat_wk_fall, 
                           family = "poisson")

# Dispersion ratio
dispersion_ratio_comm_bu <- deviance(poisson_comm_bu) / df.residual(poisson_comm_bu)
dispersion_ratio_comm_bu

# DHARMa check
sim_res_comm_bu <- simulateResiduals(fittedModel = poisson_comm_bu)
testDispersion(sim_res_comm_bu)

# Poisson version of the Bottom-Up model with target variables
poisson_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                  z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + 
                  z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_fall, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_bu_tgt <- deviance(poisson_comm_bu_tgt) / df.residual(poisson_comm_bu_tgt)
dispersion_ratio_bu_tgt

sim_res_bu_tgt <- simulateResiduals(fittedModel = poisson_comm_bu_tgt)
testDispersion(sim_res_bu_tgt)
```

Top Down
```{r}
# Poisson version of the Top-Down model without target variables
poisson_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_fall, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td <- deviance(poisson_comm_td) / df.residual(poisson_comm_td)
dispersion_ratio_td

sim_res_td <- simulateResiduals(fittedModel = poisson_comm_td)
testDispersion(sim_res_td)

# Poisson version of the Top-Down model with target variables
poisson_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_fall, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td_tgt <- deviance(poisson_comm_td_tgt) / df.residual(poisson_comm_td_tgt)
dispersion_ratio_td_tgt

sim_res_td_tgt <- simulateResiduals(fittedModel = poisson_comm_td_tgt)
testDispersion(sim_res_td_tgt)

```

Apparent Competition
```{r}
# Poisson version of the Apparent Competition model without target variables
poisson_comm_app <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_fall, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app <- deviance(poisson_comm_app) / df.residual(poisson_comm_app)
dispersion_ratio_app

sim_res_app <- simulateResiduals(fittedModel = poisson_comm_app)
testDispersion(sim_res_app)

# Poisson version of the Apparent Competition model with target variables
poisson_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_fall, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app_tgt <- deviance(poisson_comm_app_tgt) / df.residual(poisson_comm_app_tgt)
dispersion_ratio_app_tgt

sim_res_app_tgt <- simulateResiduals(fittedModel = poisson_comm_app_tgt)
testDispersion(sim_res_app_tgt)

```

#### Poisson Model Selection
```{r}
model.sel(poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt)
```

#############################################################################################

## Model Selection
```{r}
model.sel(glmm_wk_fall_null, glmm_wk_fall_wk, glmm_wk_fall_lcc_2, glmm_wk_fall_dem, glmm_wk_fall_tgt_h, glmm_wk_fall_tgt_l, glmm_wk_fall_ung, glmm_wk_fll_comm_bu, glmm_wk_fll_comm_td, glmm_wk_fll_comm_app, glmm_wk_fll_comm_bu_tgt, glmm_wk_fll_comm_td_tgt, glmm_wk_fll_comm_app_tgt, glmm_wk_fall_esker, glmm_wk_fall_comm_app_2_tgt, glmm_wk_fall_comm_app_2, glmm_wk_fall_comm_app_3, glmm_wk_fall_comm_app_3_tgt)
```

###Save Model Selection
```{r}
# Capture the model selection
#summary_output <- capture.output(model.sel(glmm_wk_fall_null, glmm_wk_fll_comm_bu, glmm_wk_fll_comm_td, glmm_wk_fll_comm_bu_tgt, glmm_wk_fll_comm_td_tgt, glmm_wk_fall_comm_app_2_tgt, glmm_wk_fall_comm_app_2, glmm_wk_fall_comm_app_3, glmm_wk_fall_comm_app_3_tgt))

# Save the model selection to a CSV file
#write.csv(summary_output, file = "Tables/region_fll_models_fnl.csv", row.names = FALSE)
```

###Save Top Model
```{r}
# Capture the summary output
#summary_output <- capture.output(summary(glmm_wk_fll_comm_bu))

# Save the summary data to a CSV file
#write.csv(summary_output, file = "Tables/region_fll_comm_bu.csv", row.names = FALSE)
```

################################################################################################################################################################################################################################################

# 4. Region, Winter detection data

```{r}
# Create a new data frame for winter
mod_dat_wk_winter <- read.csv("Processed_Data/glmm_wk_region_wtr.csv", header=T)

#reorder factor levels for categorical variables
mod_dat_wk_winter$target_cons <- fct_relevel(mod_dat_wk_winter$target_cons, "None")
mod_dat_wk_winter$target_hydro <- fct_relevel(mod_dat_wk_winter$target_hydro, "None")
mod_dat_wk_winter$target_linear <- fct_relevel(mod_dat_wk_winter$target_linear, "None")

#check levels
levels(mod_dat_wk_winter$target_cons)
levels(mod_dat_wk_winter$target_hydro)
levels(mod_dat_wk_winter$target_linear)
```

##Simple Models
```{r}
#null model
glmm_wk_wtr_null <- glmmTMB(Caribou ~ 
                     offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_wtr_null)

#week model
glmm_wk_wtr_wk <- glmmTMB(Caribou ~ 
                     week + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_wtr_wk)
```

## Target
```{r}
glmm_wk_wtr_tgt <- glmmTMB(Caribou ~ 
                     target_cons + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_winter, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_wtr_tgt)

glmm_wk_wtr_tgt_h <- glmmTMB(Caribou ~ 
                     target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_winter, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_wtr_tgt_h)

glmm_wk_wtr_tgt_l <- glmmTMB(Caribou ~ 
                     target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_winter, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_wtr_tgt_l)
```

## Committee Models

#### Bottom Up
wo target
```{r}
glmm_wk_wtr_comm_bu <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_wtr_comm_bu)
```

w target
```{r}
glmm_wk_wtr_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + target_linear + target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_wtr_comm_bu_tgt)
```

#### Top Down
wo target
```{r}
glmm_wk_wtr_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_wtr_comm_td)
```

w target
```{r}
glmm_wk_wtr_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + target_linear + target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_wtr_comm_td_tgt)
```

####Apparent Competition
wo target
```{r}
glmm_wk_wtr_comm_app <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_wtr_comm_app)
```

w target
```{r}
glmm_wk_wtr_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + target_linear + target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_wtr_comm_app_tgt)
```

#####Simplified App Comp
two sets of different simplified models to try to solve convergence issues suggested by committee.

Species Only. Species detections scaled within model formula.
######NOTE: This results in model outputs exactly the same as the unscaled ung+pred model...

wout tgt
```{r}
glmm_wk_wtr_comm_app_2 <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_wtr_comm_app_2)
```

w tgt
```{r}
glmm_wk_wtr_comm_app_2_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_wtr_comm_app_2_tgt)
```

Consolidated and scaled Ungulates (moose+muskox) and Predators (Wolves+Griz) and an interaction term for Ung*Pred

wout tgt
```{r}
glmm_wk_wtr_comm_app_3 <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_wtr_comm_app_3)
```

w tgt
```{r}
glmm_wk_wtr_comm_app_3_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + target_hydro + target_linear + (1|location_site) , data=mod_dat_wk_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_wtr_comm_app_3_tgt)
```


####Committee Model Selection
```{r}
model.sel(glmm_wk_wtr_null, glmm_wk_wtr_tgt_l, glmm_wk_wtr_tgt_h, glmm_wk_wtr_comm_bu, glmm_wk_wtr_comm_td, glmm_wk_wtr_comm_app, glmm_wk_wtr_comm_bu_tgt, glmm_wk_wtr_comm_td_tgt, glmm_wk_wtr_comm_app_tgt, glmm_wk_wtr_comm_app_2, glmm_wk_wtr_comm_app_2_tgt, glmm_wk_wtr_comm_app_3, glmm_wk_wtr_comm_app_3_tgt)
```

##############################################################################

###Over-dispersion Testing

Null Model
```{r}
# Poisson version of the random effects model
poisson_random_eff <- glmmTMB(Caribou ~ 1 + offset(log(n_days_effort)) + (1 | location_site), 
                              data = mod_dat_wk_winter, 
                              family = "poisson")

# Dispersion ratio
dispersion_ratio <- deviance(poisson_random_eff) / df.residual(poisson_random_eff)
dispersion_ratio  # >1.5 suggests overdispersion

# DHARMa check
library(DHARMa)
sim_res <- simulateResiduals(fittedModel = poisson_random_eff)
testDispersion(sim_res)
```

Bottom Up
```{r}
# Poisson version of the Bottom-Up model
poisson_comm_bu <- glmmTMB(Caribou ~ z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                           z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + 
                           offset(log(n_days_effort)) + (1 | location_site), 
                           data = mod_dat_wk_winter, 
                           family = "poisson")

# Dispersion ratio
dispersion_ratio_comm_bu <- deviance(poisson_comm_bu) / df.residual(poisson_comm_bu)
dispersion_ratio_comm_bu

# DHARMa check
sim_res_comm_bu <- simulateResiduals(fittedModel = poisson_comm_bu)
testDispersion(sim_res_comm_bu)

# Poisson version of the Bottom-Up model with target variables
poisson_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                  z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + 
                  z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_winter, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_bu_tgt <- deviance(poisson_comm_bu_tgt) / df.residual(poisson_comm_bu_tgt)
dispersion_ratio_bu_tgt

sim_res_bu_tgt <- simulateResiduals(fittedModel = poisson_comm_bu_tgt)
testDispersion(sim_res_bu_tgt)
```

Top Down
```{r}
# Poisson version of the Top-Down model without target variables
poisson_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_winter, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td <- deviance(poisson_comm_td) / df.residual(poisson_comm_td)
dispersion_ratio_td

sim_res_td <- simulateResiduals(fittedModel = poisson_comm_td)
testDispersion(sim_res_td)

# Poisson version of the Top-Down model with target variables
poisson_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_winter, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td_tgt <- deviance(poisson_comm_td_tgt) / df.residual(poisson_comm_td_tgt)
dispersion_ratio_td_tgt

sim_res_td_tgt <- simulateResiduals(fittedModel = poisson_comm_td_tgt)
testDispersion(sim_res_td_tgt)

```

Apparent Competition
```{r}
# Poisson version of the Apparent Competition model without target variables
poisson_comm_app <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_winter, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app <- deviance(poisson_comm_app) / df.residual(poisson_comm_app)
dispersion_ratio_app

sim_res_app <- simulateResiduals(fittedModel = poisson_comm_app)
testDispersion(sim_res_app)

# Poisson version of the Apparent Competition model with target variables
poisson_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_winter, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app_tgt <- deviance(poisson_comm_app_tgt) / df.residual(poisson_comm_app_tgt)
dispersion_ratio_app_tgt

sim_res_app_tgt <- simulateResiduals(fittedModel = poisson_comm_app_tgt)
testDispersion(sim_res_app_tgt)

```

#### Poisson Model Selection
```{r}
model.sel(poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt)
```

#############################################################################################

## Model Selection
```{r}
model.sel(glmm_wk_wtr_null, glmm_wk_wtr_wk, glmm_wk_wtr_lcc_2, glmm_wk_wtr_dem, glmm_wk_wtr_tgt_l, glmm_wk_wtr_tgt_h, glmm_wk_wtr_ung, glmm_wk_wtr_comm_bu, glmm_wk_wtr_comm_td, glmm_wk_wtr_comm_app, glmm_wk_wtr_comm_bu_tgt, glmm_wk_wtr_comm_td_tgt, glmm_wk_wtr_comm_app_tgt, glmm_wk_wtr_esker, glmm_wk_wtr_comm_app_2, glmm_wk_wtr_comm_app_2_tgt, glmm_wk_wtr_comm_app_3, glmm_wk_wtr_comm_app_3_tgt)
```

###Save Model Selection
```{r}
# Capture the model selection
#summary_output <- capture.output(model.sel(glmm_wk_wtr_null, glmm_wk_wtr_comm_bu, glmm_wk_wtr_comm_td, glmm_wk_wtr_comm_bu_tgt, glmm_wk_wtr_comm_td_tgt, glmm_wk_wtr_comm_app_2, glmm_wk_wtr_comm_app_2_tgt, glmm_wk_wtr_comm_app_3, glmm_wk_wtr_comm_app_3_tgt))

# Save the model selection to a CSV file
#write.csv(summary_output, file = "Tables/region_wtr_models_fnl.csv", row.names = FALSE)
```

###Save Top Model
```{r}
# Capture the summary output
#summary_output <- capture.output(summary(glmm_wk_wtr_comm_bu))

# Save the summary data to a CSV file
#write.csv(summary_output, file = "Tables/region_wtr_bu.csv", row.names = FALSE)
```

############################################################################################################################################################################################################################

# 5. Region, Spring detection data

```{r}
# Create a new data frame for winter
mod_dat_wk_spri <- read.csv("Processed_Data/glmm_wk_region_spr.csv", header=T)

#reorder factor levels for categorical variables
mod_dat_wk_spri$target_cons <- fct_relevel(mod_dat_wk_spri$target_cons, "None")
mod_dat_wk_spri$target_hydro <- fct_relevel(mod_dat_wk_spri$target_hydro, "None")
mod_dat_wk_spri$target_linear <- fct_relevel(mod_dat_wk_spri$target_linear, "None")

#check levels
levels(mod_dat_wk_spri$target_cons)
levels(mod_dat_wk_spri$target_hydro)
levels(mod_dat_wk_spri$target_linear)
```

##Simple Models
```{r}
#null model
glmm_wk_spri_null <- glmmTMB(Caribou ~ 
                     offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_spri_null)

#week model
glmm_wk_spri_wk <- glmmTMB(Caribou ~ 
                     week + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_spri_wk)
```

## Target
```{r}
glmm_wk_spri_tgt <- glmmTMB(Caribou ~ 
                     target_cons + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_spri, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_spri_tgt)

glmm_wk_spri_tgt_h <- glmmTMB(Caribou ~ 
                     target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_spri, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_spri_tgt_h)

glmm_wk_spri_tgt_l <- glmmTMB(Caribou ~ 
                     target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_spri, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_spri_tgt_l)
```

## Committee Models

Uber simple models that the committee wants run on every data set and in every season

#### Bottom Up
wo target
```{r}
glmm_wk_spr_comm_bu <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_spr_comm_bu)
```

wtarget
```{r}
glmm_wk_spr_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_spr_comm_bu_tgt)
```

#### Top Down
wo target
```{r}
glmm_wk_spr_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_spr_comm_td)
```

wtarget
```{r}
glmm_wk_spr_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_spr_comm_td_tgt)
```

####Apparent Competition
wo target
```{r}
glmm_wk_spr_comm_app <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_spr_comm_app)
```

wtarget
```{r}
glmm_wk_spr_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_spr_comm_app_tgt)
```

#####Simplified App Comp
two sets of different simplified models to try to solve convergence issues suggested by committee.

Species Only. Species detections scaled within model formula.
######NOTE: This results in model outputs exactly the same as the unscaled ung+pred model...

wout tgt
```{r}
glmm_wk_spr_comm_app_2 <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_spr_comm_app_2)
```

w tgt
```{r}
glmm_wk_spr_comm_app_2_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_spr_comm_app_2_tgt)
```

Consolidated and scaled Ungulates (moose+muskox) and Predators (Wolves+Griz) and an interaction term for Ung*Pred

wout tgt
```{r}
glmm_wk_spr_comm_app_3 <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_spr_comm_app_3)
```

w tgt
```{r}
glmm_wk_spr_comm_app_3_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + target_hydro + target_linear + (1|location_site) , data=mod_dat_wk_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_spr_comm_app_3_tgt)
```


####Committee Model Selection
```{r}
model.sel(glmm_wk_spri_null, glmm_wk_spri_tgt_h, glmm_wk_spri_tgt_l, glmm_wk_spr_comm_bu, glmm_wk_spr_comm_td, glmm_wk_spr_comm_app, glmm_wk_spr_comm_bu_tgt, glmm_wk_spr_comm_td_tgt, glmm_wk_spr_comm_app_tgt, glmm_wk_spr_comm_app_2, glmm_wk_spr_comm_app_2_tgt, glmm_wk_spr_comm_app_3, glmm_wk_spr_comm_app_3_tgt)
```

##############################################################################

###Over-dispersion Testing

Null Model
```{r}
# Poisson version of the random effects model
poisson_random_eff <- glmmTMB(Caribou ~ 1 + offset(log(n_days_effort)) + (1 | location_site), 
                              data = mod_dat_wk_spri, 
                              family = "poisson")

# Dispersion ratio
dispersion_ratio <- deviance(poisson_random_eff) / df.residual(poisson_random_eff)
dispersion_ratio  # >1.5 suggests overdispersion

# DHARMa check
library(DHARMa)
sim_res <- simulateResiduals(fittedModel = poisson_random_eff)
testDispersion(sim_res)
```

Bottom Up
```{r}
# Poisson version of the Bottom-Up model
poisson_comm_bu <- glmmTMB(Caribou ~ z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                           z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + 
                           offset(log(n_days_effort)) + (1 | location_site), 
                           data = mod_dat_wk_spri, 
                           family = "poisson")

# Dispersion ratio
dispersion_ratio_comm_bu <- deviance(poisson_comm_bu) / df.residual(poisson_comm_bu)
dispersion_ratio_comm_bu

# DHARMa check
sim_res_comm_bu <- simulateResiduals(fittedModel = poisson_comm_bu)
testDispersion(sim_res_comm_bu)

# Poisson version of the Bottom-Up model with target variables
poisson_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                  z.X300_MF + z.X300_TSPS + z.X300_TSPG + z.X300_BAR + 
                  z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_spri, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_bu_tgt <- deviance(poisson_comm_bu_tgt) / df.residual(poisson_comm_bu_tgt)
dispersion_ratio_bu_tgt

sim_res_bu_tgt <- simulateResiduals(fittedModel = poisson_comm_bu_tgt)
testDispersion(sim_res_bu_tgt)
```

Top Down
```{r}
# Poisson version of the Top-Down model without target variables
poisson_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_spri, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td <- deviance(poisson_comm_td) / df.residual(poisson_comm_td)
dispersion_ratio_td

sim_res_td <- simulateResiduals(fittedModel = poisson_comm_td)
testDispersion(sim_res_td)

# Poisson version of the Top-Down model with target variables
poisson_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_spri, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td_tgt <- deviance(poisson_comm_td_tgt) / df.residual(poisson_comm_td_tgt)
dispersion_ratio_td_tgt

sim_res_td_tgt <- simulateResiduals(fittedModel = poisson_comm_td_tgt)
testDispersion(sim_res_td_tgt)

```

Apparent Competition
```{r}
# Poisson version of the Apparent Competition model without target variables
poisson_comm_app <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_spri, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app <- deviance(poisson_comm_app) / df.residual(poisson_comm_app)
dispersion_ratio_app

sim_res_app <- simulateResiduals(fittedModel = poisson_comm_app)
testDispersion(sim_res_app)

# Poisson version of the Apparent Competition model with target variables
poisson_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_spri, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app_tgt <- deviance(poisson_comm_app_tgt) / df.residual(poisson_comm_app_tgt)
dispersion_ratio_app_tgt

sim_res_app_tgt <- simulateResiduals(fittedModel = poisson_comm_app_tgt)
testDispersion(sim_res_app_tgt)

```

#### Poisson Model Selection
```{r}
model.sel(poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt)
```

#############################################################################################

## Model Selection
```{r}
model.sel(glmm_wk_spri_null, glmm_wk_spri_tgt_h, glmm_wk_spri_tgt_l, glmm_wk_spr_comm_bu, glmm_wk_spr_comm_td, glmm_wk_spr_comm_app, glmm_wk_spr_comm_bu_tgt, glmm_wk_spr_comm_td_tgt, glmm_wk_spr_comm_app_tgt, glmm_wk_spr_comm_app_2, glmm_wk_spr_comm_app_2_tgt, glmm_wk_spr_comm_app_3, glmm_wk_spr_comm_app_3_tgt, poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt)
```

###Save Model Selection
```{r}
# Capture the model selection
#summary_output <- capture.output(model.sel(glmm_wk_spri_null, glmm_wk_spr_comm_bu, glmm_wk_spr_comm_td, glmm_wk_spr_comm_bu_tgt, glmm_wk_spr_comm_td_tgt, glmm_wk_spr_comm_app_2, glmm_wk_spr_comm_app_2_tgt, glmm_wk_spr_comm_app_3, glmm_wk_spr_comm_app_3_tgt))

# Save the model selection to a CSV file
#write.csv(summary_output, file = "Tables/region_spr_models_fnl.csv", row.names = FALSE)
```

###Save Top Model
```{r}
# Capture the summary output
#summary_output <- capture.output(summary(glmm_wk_spr_comm_bu_tgt))

# Save the summary data to a CSV file
#write.csv(summary_output, file = "Tables/region_spr_comm_bu_tgt.csv", row.names = FALSE)
```

################################################################################################################################################################################################################################################################################################

#6. Local, Multiseason, WEEK

Let's look at the same sampling periods (i.e. seasons) at the local extent only to see if things change.

Predicting that habitat associations will be more varied (less stark contrast between taiga and tundra) and that other processes might be more influential than bottom-up.

```{r}
mod_dat_wk_cbou <- read.csv("Processed_Data/glmm_wk_local_multi.csv", header=T)

#reorder factor levels for categorical variables
mod_dat_wk_cbou$target_cons <- fct_relevel(mod_dat_wk_cbou$target_cons, "None")
mod_dat_wk_cbou$target_hydro <- fct_relevel(mod_dat_wk_cbou$target_hydro, "None")
mod_dat_wk_cbou$target_linear <- fct_relevel(mod_dat_wk_cbou$target_linear, "None")

#check levels
levels(mod_dat_wk_cbou$target_cons)
levels(mod_dat_wk_cbou$target_hydro)
levels(mod_dat_wk_cbou$target_linear)
```

##Simple Models
```{r}
#GLMM with random and survey effort
glmm_wk_cbou_null <- glmmTMB(Caribou ~ 1 +  offset(log(n_days_effort)) + (1 | location_site) , data = mod_dat_wk_cbou, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_null)

#with week
glmm_wk_cbou_wk <- glmmTMB(Caribou ~ week + offset(log(n_days_effort)) + (1 | location_site) , data = mod_dat_wk_cbou, family="nbinom2", control=glmmTMBControl(parallel=5))
```

## Target
```{r}
glmm_wk_cbou_tgt <- glmmTMB(Caribou ~ 
                     target_cons + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_cbou_tgt)

glmm_wk_cbou_tgt_h <- glmmTMB(Caribou ~ 
                     target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_cbou_tgt_h)

glmm_wk_cbou_tgt_l <- glmmTMB(Caribou ~ 
                     target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_cbou_tgt_l)
```

## Committee Models

### Bottom Up

####NOTE: At the local scale, SPTNF, TSPBDF, and TSPS account for less than 1% of total area captured within buffer areas and were thus omitted.

SPPSLM accounts for 44% of the total buffer area at the local scale and will be used as the reference level and thus ommitted from the model. 

wo target
```{r}
glmm_wk_cbou_comm_bu <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_comm_bu)
```

wtarget
```{r}
glmm_wk_cbou_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_SPPSLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_comm_bu_tgt)
```

### Top Down
wo target
```{r}
glmm_wk_cbou_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_comm_td)
```

wtarget
```{r}
glmm_wk_cbou_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_comm_td_tgt)
```

###Apparent Competition
wo target
```{r}
glmm_wk_cbou_comm_app <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_comm_app)
```

wtarget
```{r}
glmm_wk_cbou_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_comm_app_tgt)
```

#####Simplified App Comp
two sets of different simplified models to try to solve convergence issues suggested by committee.

Species Only. Species detections scaled within model formula.
######NOTE: This results in model outputs exactly the same as the unscaled ung+pred model...

wout tgt
```{r}
glmm_wk_cbou_comm_app_2 <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_comm_app_2)
```

w tgt
```{r}
glmm_wk_cbou_comm_app_2_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_comm_app_2_tgt)
```

Consolidated and scaled Ungulates (moose+muskox) and Predators (Wolves+Griz) and an interaction term for Ung*Pred

wout tgt
```{r}
glmm_wk_cbou_comm_app_3 <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_comm_app_3)
```

w tgt
```{r}
glmm_wk_cbou_comm_app_3_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + target_hydro + target_linear + (1|location_site) , data=mod_dat_wk_cbou, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_comm_app_3_tgt)
```

###Committee Model Selection
```{r}
model.sel(glmm_wk_cbou_null, glmm_wk_cbou_wk, glmm_wk_cbou_tgt_l, glmm_wk_cbou_tgt_h, glmm_wk_cbou_comm_bu, glmm_wk_cbou_comm_td, glmm_wk_cbou_comm_app, glmm_wk_cbou_comm_bu_tgt, glmm_wk_cbou_comm_td_tgt, glmm_wk_cbou_comm_app_tgt, glmm_wk_cbou_comm_app_2, glmm_wk_cbou_comm_app_2_tgt, glmm_wk_cbou_comm_app_3, glmm_wk_cbou_comm_app_3_tgt)
```

##############################################################################

###Over-dispersion Testing

Null Model
```{r}
# Poisson version of the random effects model
poisson_random_eff <- glmmTMB(Caribou ~ 1 + offset(log(n_days_effort)) + (1 | location_site), 
                              data = mod_dat_wk_cbou, 
                              family = "poisson")

# Dispersion ratio
dispersion_ratio <- deviance(poisson_random_eff) / df.residual(poisson_random_eff)
dispersion_ratio  # >1.5 suggests overdispersion

# DHARMa check
library(DHARMa)
sim_res <- simulateResiduals(fittedModel = poisson_random_eff)
testDispersion(sim_res)
```

Bottom Up
```{r}
# Poisson version of the Bottom-Up model
poisson_comm_bu <- glmmTMB(Caribou ~ z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                           z.X300_MF + z.X300_TSPG + z.X300_BAR + 
                           offset(log(n_days_effort)) + (1 | location_site), 
                           data = mod_dat_wk_cbou, 
                           family = "poisson")

# Dispersion ratio
dispersion_ratio_comm_bu <- deviance(poisson_comm_bu) / df.residual(poisson_comm_bu)
dispersion_ratio_comm_bu

# DHARMa check
sim_res_comm_bu <- simulateResiduals(fittedModel = poisson_comm_bu)
testDispersion(sim_res_comm_bu)

# Poisson version of the Bottom-Up model with target variables
poisson_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                  z.X300_MF + z.X300_TSPG + z.X300_BAR + 
                  z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_bu_tgt <- deviance(poisson_comm_bu_tgt) / df.residual(poisson_comm_bu_tgt)
dispersion_ratio_bu_tgt

sim_res_bu_tgt <- simulateResiduals(fittedModel = poisson_comm_bu_tgt)
testDispersion(sim_res_bu_tgt)
```

Top Down
```{r}
# Poisson version of the Top-Down model without target variables
poisson_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td <- deviance(poisson_comm_td) / df.residual(poisson_comm_td)
dispersion_ratio_td

sim_res_td <- simulateResiduals(fittedModel = poisson_comm_td)
testDispersion(sim_res_td)

# Poisson version of the Top-Down model with target variables
poisson_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td_tgt <- deviance(poisson_comm_td_tgt) / df.residual(poisson_comm_td_tgt)
dispersion_ratio_td_tgt

sim_res_td_tgt <- simulateResiduals(fittedModel = poisson_comm_td_tgt)
testDispersion(sim_res_td_tgt)

```

Apparent Competition
```{r}
# Poisson version of the Apparent Competition model without target variables
poisson_comm_app <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app <- deviance(poisson_comm_app) / df.residual(poisson_comm_app)
dispersion_ratio_app

sim_res_app <- simulateResiduals(fittedModel = poisson_comm_app)
testDispersion(sim_res_app)

# Poisson version of the Apparent Competition model with target variables
poisson_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app_tgt <- deviance(poisson_comm_app_tgt) / df.residual(poisson_comm_app_tgt)
dispersion_ratio_app_tgt

sim_res_app_tgt <- simulateResiduals(fittedModel = poisson_comm_app_tgt)
testDispersion(sim_res_app_tgt)

```

#### Poisson Model Selection
```{r}
model.sel(poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt)
```

#############################################################################################

## Model Selection
```{r}
model.sel(glmm_wk_cbou_null, glmm_wk_cbou_wk, glmm_wk_cbou_tgt_l, glmm_wk_cbou_tgt_h, glmm_wk_cbou_comm_bu, glmm_wk_cbou_comm_td, glmm_wk_cbou_comm_app, glmm_wk_cbou_comm_bu_tgt, glmm_wk_cbou_comm_td_tgt, glmm_wk_cbou_comm_app_tgt, glmm_wk_cbou_comm_app_2, glmm_wk_cbou_comm_app_2_tgt, glmm_wk_cbou_comm_app_3, glmm_wk_cbou_comm_app_3_tgt, poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt)
```

###Save Model Selection
```{r}
# Capture the model selection
#summary_output <- capture.output(model.sel(glmm_wk_cbou_null, glmm_wk_cbou_wk, glmm_wk_cbou_comm_bu, glmm_wk_cbou_comm_td, glmm_wk_cbou_comm_bu_tgt, glmm_wk_cbou_comm_td_tgt, glmm_wk_cbou_comm_app_2, glmm_wk_cbou_comm_app_2_tgt, glmm_wk_cbou_comm_app_3, glmm_wk_cbou_comm_app_3_tgt))

# Save the model selection to a CSV file
#write.csv(summary_output, file = "Tables/local_multi_models_fnl.csv", row.names = FALSE)
```

###Save Top Model
```{r}
# Capture the summary output
#summary_output <- capture.output(summary(glmm_wk_cbou_wk))

# Save the summary data to a CSV file
#write.csv(summary_output, file = "Tables/local_multi_wk.csv", row.names = FALSE)
```

################################################################################################################################################################################################

#7. Local, Summer, WEEKLY detection data
```{r}
# Create a new data frame for summer
mod_dat_wk_cbou_summer <- read.csv("Processed_Data/glmm_wk_local_smr.csv", header=T)

#reorder factor levels for categorical variables
mod_dat_wk_cbou_summer$target_cons <- fct_relevel(mod_dat_wk_cbou_summer$target_cons, "None")
mod_dat_wk_cbou_summer$target_hydro <- fct_relevel(mod_dat_wk_cbou_summer$target_hydro, "None")
mod_dat_wk_cbou_summer$target_linear <- fct_relevel(mod_dat_wk_cbou_summer$target_linear, "None")

#check levels
levels(mod_dat_wk_cbou_summer$target_cons)
levels(mod_dat_wk_cbou_summer$target_hydro)
levels(mod_dat_wk_cbou_summer$target_linear)
```

##Simple Models
```{r}
#null model
glmm_wk_cbou_smr_null <- glmmTMB(Caribou ~ 
                     offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_smr_null)

#week model
glmm_wk_cbou_smr_wk <- glmmTMB(Caribou ~ 
                     week + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_smr_wk)
```

## Target
```{r}
glmm_wk_cbou_smr_tgt <- glmmTMB(Caribou ~ 
                     target_cons + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_summer, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_cbou_smr_tgt)

glmm_wk_cbou_smr_tgt_h <- glmmTMB(Caribou ~ 
                     target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_summer, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_cbou_smr_tgt_h)

glmm_wk_cbou_smr_tgt_l <- glmmTMB(Caribou ~ 
                     target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_summer, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_cbou_smr_tgt_l)
```

## Committee Models

#### Bottom Up
wo target
```{r}
glmm_wk_cbou_smr_comm_bu <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_smr_comm_bu)
```

w target
```{r}
glmm_wk_cbou_smr_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_smr_comm_bu_tgt)
```

#### Top Down
wo target
```{r}
glmm_wk_cbou_smr_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_smr_comm_td)
```

w target
```{r}
glmm_wk_cbou_smr_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_smr_comm_td_tgt)
```

####Apparent Competition
wo target
```{r}
glmm_wk_cbou_smr_comm_app <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_smr_comm_app)
```

w target
```{r}
glmm_wk_cbou_smr_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_smr_comm_app_tgt)
```

#####Simplified App Comp
two sets of different simplified models to try to solve convergence issues suggested by committee.

Species Only. Species detections scaled within model formula.
######NOTE: This results in model outputs exactly the same as the unscaled ung+pred model...

wout tgt
```{r}
glmm_wk_cbou_smr_comm_app_2 <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_smr_comm_app_2)
```

w tgt
```{r}
glmm_wk_cbou_smr_comm_app_2_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_smr_comm_app_2_tgt)
```

Consolidated and scaled Ungulates (moose+muskox) and Predators (Wolves+Griz) and an interaction term for Ung*Pred

wout tgt
```{r}
glmm_wk_cbou_smr_comm_app_3 <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_smr_comm_app_3)
```

w tgt
```{r}
glmm_wk_cbou_smr_comm_app_3_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + target_hydro + target_linear + (1|location_site) , data=mod_dat_wk_cbou_summer, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_smr_comm_app_3_tgt)
```


####Committee Model Selection
```{r}
model.sel(glmm_wk_cbou_smr_null, glmm_wk_cbou_smr_wk, glmm_wk_cbou_smr_tgt_h, glmm_wk_cbou_smr_tgt_l, glmm_wk_cbou_smr_comm_bu, glmm_wk_cbou_smr_comm_td, glmm_wk_cbou_smr_comm_app, glmm_wk_cbou_smr_comm_bu_tgt, glmm_wk_cbou_smr_comm_td_tgt, glmm_wk_cbou_smr_comm_app_tgt, glmm_wk_cbou_smr_comm_app_2, glmm_wk_cbou_smr_comm_app_2_tgt, glmm_wk_cbou_smr_comm_app_3, glmm_wk_cbou_smr_comm_app_3_tgt)
```

##############################################################################

###Over-dispersion Testing

Null Model
```{r}
# Poisson version of the random effects model
poisson_random_eff <- glmmTMB(Caribou ~ 1 + offset(log(n_days_effort)) + (1 | location_site), 
                              data = mod_dat_wk_cbou_summer, 
                              family = "poisson")

# Dispersion ratio
dispersion_ratio <- deviance(poisson_random_eff) / df.residual(poisson_random_eff)
dispersion_ratio  # >1.5 suggests overdispersion

# DHARMa check
library(DHARMa)
sim_res <- simulateResiduals(fittedModel = poisson_random_eff)
testDispersion(sim_res)
```

Bottom Up
```{r}
# Poisson version of the Bottom-Up model
poisson_comm_bu <- glmmTMB(Caribou ~ z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                           z.X300_MF + z.X300_TSPG + z.X300_BAR + 
                           offset(log(n_days_effort)) + (1 | location_site), 
                           data = mod_dat_wk_cbou_summer, 
                           family = "poisson")

# Dispersion ratio
dispersion_ratio_comm_bu <- deviance(poisson_comm_bu) / df.residual(poisson_comm_bu)
dispersion_ratio_comm_bu

# DHARMa check
sim_res_comm_bu <- simulateResiduals(fittedModel = poisson_comm_bu)
testDispersion(sim_res_comm_bu)

# Poisson version of the Bottom-Up model with target variables
poisson_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                  z.X300_MF + z.X300_TSPG + z.X300_BAR + 
                  z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_summer, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_bu_tgt <- deviance(poisson_comm_bu_tgt) / df.residual(poisson_comm_bu_tgt)
dispersion_ratio_bu_tgt

sim_res_bu_tgt <- simulateResiduals(fittedModel = poisson_comm_bu_tgt)
testDispersion(sim_res_bu_tgt)
```

Top Down
```{r}
# Poisson version of the Top-Down model without target variables
poisson_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_summer, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td <- deviance(poisson_comm_td) / df.residual(poisson_comm_td)
dispersion_ratio_td

sim_res_td <- simulateResiduals(fittedModel = poisson_comm_td)
testDispersion(sim_res_td)

# Poisson version of the Top-Down model with target variables
poisson_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_summer, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td_tgt <- deviance(poisson_comm_td_tgt) / df.residual(poisson_comm_td_tgt)
dispersion_ratio_td_tgt

sim_res_td_tgt <- simulateResiduals(fittedModel = poisson_comm_td_tgt)
testDispersion(sim_res_td_tgt)

```

Apparent Competition
```{r}
# Poisson version of the Apparent Competition model without target variables
poisson_comm_app <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_summer, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app <- deviance(poisson_comm_app) / df.residual(poisson_comm_app)
dispersion_ratio_app

sim_res_app <- simulateResiduals(fittedModel = poisson_comm_app)
testDispersion(sim_res_app)

# Poisson version of the Apparent Competition model with target variables
poisson_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_summer, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app_tgt <- deviance(poisson_comm_app_tgt) / df.residual(poisson_comm_app_tgt)
dispersion_ratio_app_tgt

sim_res_app_tgt <- simulateResiduals(fittedModel = poisson_comm_app_tgt)
testDispersion(sim_res_app_tgt)

```

#### Poisson Model Selection
```{r}
model.sel(poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt)
```


#############################################################################################

## Model Selection
```{r}
model.sel(glmm_wk_cbou_smr_null, glmm_wk_cbou_smr_wk, glmm_wk_cbou_smr_tgt_h, glmm_wk_cbou_smr_tgt_l, glmm_wk_cbou_smr_comm_bu, glmm_wk_cbou_smr_comm_td, glmm_wk_cbou_smr_comm_app, glmm_wk_cbou_smr_comm_bu_tgt, glmm_wk_cbou_smr_comm_td_tgt, glmm_wk_cbou_smr_comm_app_tgt, glmm_wk_cbou_smr_comm_app_2, glmm_wk_cbou_smr_comm_app_2_tgt, glmm_wk_cbou_smr_comm_app_3, glmm_wk_cbou_smr_comm_app_3_tgt,poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt)
```

###Save Model Selection
```{r}
# Capture the model selection
#summary_output <- capture.output(model.sel(glmm_wk_cbou_smr_null, glmm_wk_cbou_smr_comm_bu, glmm_wk_cbou_smr_comm_td, glmm_wk_cbou_smr_comm_bu_tgt, glmm_wk_cbou_smr_comm_td_tgt, glmm_wk_cbou_smr_comm_app_2, glmm_wk_cbou_smr_comm_app_2_tgt, glmm_wk_cbou_smr_comm_app_3, glmm_wk_cbou_smr_comm_app_3_tgt))

# Save the model selection to a CSV file
#write.csv(summary_output, file = "Tables/local_smr_models_fnl.csv", row.names = FALSE)
```

###Save Top Model
```{r}
# Capture the summary output
#summary_output <- capture.output(summary(glmm_wk_cbou_smr_comm_bu_tgt))

# Save the summary data to a CSV file
#write.csv(summary_output, file = "Tables/local_smr_comm_bu_tgt.csv", row.names = FALSE)
```

################################################################################################################################################################################################

# 8. Local, Fall, WEEKLY detection data
```{r}
# Create a new data frame for winter
mod_dat_wk_cbou_fall <- read.csv("Processed_Data/glmm_wk_local_fall.csv", header=T)

#reorder factor levels for categorical variables
mod_dat_wk_cbou_fall$target_cons <- fct_relevel(mod_dat_wk_cbou_fall$target_cons, "None")
mod_dat_wk_cbou_fall$target_hydro <- fct_relevel(mod_dat_wk_cbou_fall$target_hydro, "None")
mod_dat_wk_cbou_fall$target_linear <- fct_relevel(mod_dat_wk_cbou_fall$target_linear, "None")

#check levels
levels(mod_dat_wk_cbou_fall$target_cons)
levels(mod_dat_wk_cbou_fall$target_hydro)
levels(mod_dat_wk_cbou_fall$target_linear)
```

##Simple Models
```{r}
#null model
glmm_wk_cbou_fall_null <- glmmTMB(Caribou ~ 
                     offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_fall_null)

#week model
glmm_wk_cbou_fall_wk <- glmmTMB(Caribou ~ 
                     week + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_fall_wk)
```

## Target
```{r}
glmm_wk_cbou_fall_tgt <- glmmTMB(Caribou ~ 
                     target_cons + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_fall_tgt)

glmm_wk_cbou_fall_tgt_h <- glmmTMB(Caribou ~ 
                     target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_fall_tgt_h)

glmm_wk_cbou_fall_tgt_l <- glmmTMB(Caribou ~ 
                     target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_fall_tgt_l)
```

## Committee Models

#### Bottom Up
wo target
```{r}
glmm_wk_cbou_fll_comm_bu <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_fll_comm_bu)
```

w tgt
```{r}
glmm_wk_cbou_fll_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_fll_comm_bu_tgt)
```

#### Top Down
wo tgt
```{r}
glmm_wk_cbou_fll_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_fll_comm_td)
```

w tgt
```{r}
glmm_wk_cbou_fll_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_fll_comm_td_tgt)
```

####Apparent Competition
wo target
```{r}
glmm_wk_cbou_fll_comm_app <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_fll_comm_app)
```

w target
```{r}
glmm_wk_cbou_fll_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_fll_comm_app_tgt)
```

#####Simplified App Comp
two sets of different simplified models to try to solve convergence issues suggested by committee.

Species Only. Species detections scaled within model formula.
######NOTE: This results in model outputs exactly the same as the unscaled ung+pred model...

wout tgt
```{r}
glmm_wk_cbou_fll_comm_app_2 <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_fll_comm_app_2)
```

w tgt
```{r}
glmm_wk_cbou_fll_comm_app_2_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_fll_comm_app_2_tgt)
```

Consolidated and scaled Ungulates (moose+muskox) and Predators (Wolves+Griz) and an interaction term for Ung*Pred

wout tgt
```{r}
glmm_wk_cbou_fll_comm_app_3 <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_fll_comm_app_3)
```

w tgt
```{r}
glmm_wk_cbou_fll_comm_app_3_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + target_hydro + target_linear + (1|location_site) , data=mod_dat_wk_cbou_fall, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_fll_comm_app_3_tgt)
```


####Committee Model Selection
```{r}
model.sel(glmm_wk_cbou_fall_null, glmm_wk_cbou_fall_wk, glmm_wk_cbou_fall_tgt_h, glmm_wk_cbou_fall_tgt_l, glmm_wk_cbou_fll_comm_bu, glmm_wk_cbou_fll_comm_td, glmm_wk_cbou_fll_comm_app, glmm_wk_cbou_fll_comm_bu_tgt, glmm_wk_cbou_fll_comm_td_tgt, glmm_wk_cbou_fll_comm_app_tgt, glmm_wk_cbou_fll_comm_app_2, glmm_wk_cbou_fll_comm_app_2_tgt, glmm_wk_cbou_fll_comm_app_3, glmm_wk_cbou_fll_comm_app_3_tgt)
```

#############################################################################################

###Over-dispersion Testing

Null Model
```{r}
# Poisson version of the random effects model
poisson_random_eff <- glmmTMB(Caribou ~ 1 + offset(log(n_days_effort)) + (1 | location_site), 
                              data = mod_dat_wk_cbou_fall, 
                              family = "poisson")

# Dispersion ratio
dispersion_ratio <- deviance(poisson_random_eff) / df.residual(poisson_random_eff)
dispersion_ratio  # >1.5 suggests overdispersion

# DHARMa check
library(DHARMa)
sim_res <- simulateResiduals(fittedModel = poisson_random_eff)
testDispersion(sim_res)
```

Bottom Up
```{r}
# Poisson version of the Bottom-Up model
poisson_comm_bu <- glmmTMB(Caribou ~ z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                           z.X300_MF + z.X300_TSPG + z.X300_BAR + 
                           offset(log(n_days_effort)) + (1 | location_site), 
                           data = mod_dat_wk_cbou_fall, 
                           family = "poisson")

# Dispersion ratio
dispersion_ratio_comm_bu <- deviance(poisson_comm_bu) / df.residual(poisson_comm_bu)
dispersion_ratio_comm_bu

# DHARMa check
sim_res_comm_bu <- simulateResiduals(fittedModel = poisson_comm_bu)
testDispersion(sim_res_comm_bu)

# Poisson version of the Bottom-Up model with target variables
poisson_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                  z.X300_MF + z.X300_TSPG + z.X300_BAR + 
                  z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_fall, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_bu_tgt <- deviance(poisson_comm_bu_tgt) / df.residual(poisson_comm_bu_tgt)
dispersion_ratio_bu_tgt

sim_res_bu_tgt <- simulateResiduals(fittedModel = poisson_comm_bu_tgt)
testDispersion(sim_res_bu_tgt)
```

Top Down
```{r}
# Poisson version of the Top-Down model without target variables
poisson_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_fall, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td <- deviance(poisson_comm_td) / df.residual(poisson_comm_td)
dispersion_ratio_td

sim_res_td <- simulateResiduals(fittedModel = poisson_comm_td)
testDispersion(sim_res_td)

# Poisson version of the Top-Down model with target variables
poisson_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_fall, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td_tgt <- deviance(poisson_comm_td_tgt) / df.residual(poisson_comm_td_tgt)
dispersion_ratio_td_tgt

sim_res_td_tgt <- simulateResiduals(fittedModel = poisson_comm_td_tgt)
testDispersion(sim_res_td_tgt)

```

Apparent Competition
```{r}
# Poisson version of the Apparent Competition model without target variables
poisson_comm_app <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_fall, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app <- deviance(poisson_comm_app) / df.residual(poisson_comm_app)
dispersion_ratio_app

sim_res_app <- simulateResiduals(fittedModel = poisson_comm_app)
testDispersion(sim_res_app)

# Poisson version of the Apparent Competition model with target variables
poisson_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_fall, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app_tgt <- deviance(poisson_comm_app_tgt) / df.residual(poisson_comm_app_tgt)
dispersion_ratio_app_tgt

sim_res_app_tgt <- simulateResiduals(fittedModel = poisson_comm_app_tgt)
testDispersion(sim_res_app_tgt)

```

#### Poisson Model Selection
```{r}
model.sel(poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt)
```

################################################################################

## Model Selection
```{r}
model.sel(glmm_wk_cbou_fall_null, glmm_wk_cbou_fall_wk, glmm_wk_cbou_fall_tgt_h, glmm_wk_cbou_fall_tgt_l, glmm_wk_cbou_fll_comm_bu, glmm_wk_cbou_fll_comm_td, glmm_wk_cbou_fll_comm_app, glmm_wk_cbou_fll_comm_bu_tgt, glmm_wk_cbou_fll_comm_td_tgt, glmm_wk_cbou_fll_comm_app_tgt, glmm_wk_cbou_fll_comm_app_2, glmm_wk_cbou_fll_comm_app_2_tgt, glmm_wk_cbou_fll_comm_app_3, glmm_wk_cbou_fll_comm_app_3_tgt,poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt)
```

###Save Model Selection
```{r}
# Capture the model selection
#summary_output <- capture.output(model.sel(glmm_wk_cbou_fall_null, glmm_wk_cbou_fll_comm_bu, glmm_wk_cbou_fll_comm_td, glmm_wk_cbou_fll_comm_bu_tgt, glmm_wk_cbou_fll_comm_td_tgt, glmm_wk_cbou_fll_comm_app_2, glmm_wk_cbou_fll_comm_app_2_tgt, glmm_wk_cbou_fll_comm_app_3, glmm_wk_cbou_fll_comm_app_3_tgt))

# Save the model selection to a CSV file
#write.csv(summary_output, file = "Tables/local_fll_models_fnl.csv", row.names = FALSE)
```

###Save Top Model
```{r}
# Capture the summary output
#summary_output <- capture.output(summary(glmm_wk_cbou_fll_comm_bu))

# Save the summary data to a CSV file
#write.csv(summary_output, file = "Tables/local_fll_comm_bu.csv", row.names = FALSE)
```

################################################################################################################################################################################################

# 9. Local, Winter, WEEKLY detection data
```{r}
# Create a new data frame for winter
mod_dat_wk_cbou_winter <- read.csv("Processed_Data/glmm_wk_local_wtr.csv", header=T)

#reorder factor levels for categorical variables
mod_dat_wk_cbou_winter$target_cons <- fct_relevel(mod_dat_wk_cbou_winter$target_cons, "None")
mod_dat_wk_cbou_winter$target_hydro <- fct_relevel(mod_dat_wk_cbou_winter$target_hydro, "None")
mod_dat_wk_cbou_winter$target_linear <- fct_relevel(mod_dat_wk_cbou_winter$target_linear, "None")

#check levels
levels(mod_dat_wk_cbou_winter$target_cons)
levels(mod_dat_wk_cbou_winter$target_hydro)
levels(mod_dat_wk_cbou_winter$target_linear)
```

##Simple Models
```{r}
#null model
glmm_wk_cbou_wtr_null <- glmmTMB(Caribou ~ 
                     offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_wtr_null)

#week model
glmm_wk_cbou_wtr_wk <- glmmTMB(Caribou ~ 
                     week + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_wtr_wk)
```

## Target
```{r}
glmm_wk_cbou_wtr_tgt <- glmmTMB(Caribou ~ 
                     target_cons + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_winter, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_cbou_wtr_tgt)

glmm_wk_cbou_wtr_tgt_h <- glmmTMB(Caribou ~ 
                     target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_winter, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_cbou_wtr_tgt_h)

glmm_wk_cbou_wtr_tgt_l <- glmmTMB(Caribou ~ 
                     target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_winter, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_cbou_wtr_tgt_l)
```

## Committee Models

#### Bottom Up
wo tgt
```{r}
glmm_wk_cbou_wtr_comm_bu <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_wtr_comm_bu)
```

w tgt
```{r}
glmm_wk_cbou_wtr_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_wtr_comm_bu_tgt)
```

#### Top Down
wo tgt
```{r}
glmm_wk_cbou_wtr_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_wtr_comm_td)
```

w tgt
```{r}
glmm_wk_cbou_wtr_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf)+ target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_wtr_comm_td_tgt)
```

####Apparent Competition
wo tgt
```{r}
glmm_wk_cbou_wtr_comm_app <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_wtr_comm_app)
```

w tgt
```{r}
glmm_wk_cbou_wtr_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_wtr_comm_app_tgt)
```

#####Simplified App Comp
two sets of different simplified models to try to solve convergence issues suggested by committee.

Species Only. Species detections scaled within model formula.
######NOTE: This results in model outputs exactly the same as the unscaled ung+pred model...

wout tgt
```{r}
glmm_wk_cbou_wtr_comm_app_2 <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_wtr_comm_app_2)
```

w tgt
```{r}
glmm_wk_cbou_wtr_comm_app_2_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_wtr_comm_app_2_tgt)
```

Consolidated and scaled Ungulates (moose+muskox) and Predators (Wolves+Griz) and an interaction term for Ung*Pred

wout tgt
```{r}
glmm_wk_cbou_wtr_comm_app_3 <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_wtr_comm_app_3)
```

w tgt
```{r}
glmm_wk_cbou_wtr_comm_app_3_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + target_hydro + target_linear + (1|location_site) , data=mod_dat_wk_cbou_winter, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_wtr_comm_app_3_tgt)
```

####Committee Model Selection
```{r}
model.sel(glmm_wk_cbou_wtr_null, glmm_wk_cbou_wtr_tgt_h, glmm_wk_cbou_wtr_tgt_l, glmm_wk_cbou_wtr_comm_bu, glmm_wk_cbou_wtr_comm_td, glmm_wk_cbou_wtr_comm_app, glmm_wk_cbou_wtr_comm_bu_tgt, glmm_wk_cbou_wtr_comm_td_tgt, glmm_wk_cbou_wtr_comm_app_tgt, glmm_wk_cbou_wtr_comm_app_2, glmm_wk_cbou_wtr_comm_app_2_tgt, glmm_wk_cbou_wtr_comm_app_3, glmm_wk_cbou_wtr_comm_app_3_tgt)
```

###################################################################################

###Over-dispersion Testing

Null Model
```{r}
# Poisson version of the random effects model
poisson_random_eff <- glmmTMB(Caribou ~ 1 + offset(log(n_days_effort)) + (1 | location_site), 
                              data = mod_dat_wk_cbou_winter, 
                              family = "poisson")

# Dispersion ratio
dispersion_ratio <- deviance(poisson_random_eff) / df.residual(poisson_random_eff)
dispersion_ratio  # >1.5 suggests overdispersion

# DHARMa check
library(DHARMa)
sim_res <- simulateResiduals(fittedModel = poisson_random_eff)
testDispersion(sim_res)
```

Bottom Up
```{r}
# Poisson version of the Bottom-Up model
poisson_comm_bu <- glmmTMB(Caribou ~ z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                           z.X300_MF + z.X300_TSPG + z.X300_BAR + 
                           offset(log(n_days_effort)) + (1 | location_site), 
                           data = mod_dat_wk_cbou_winter, 
                           family = "poisson")

# Dispersion ratio
dispersion_ratio_comm_bu <- deviance(poisson_comm_bu) / df.residual(poisson_comm_bu)
dispersion_ratio_comm_bu

# DHARMa check
sim_res_comm_bu <- simulateResiduals(fittedModel = poisson_comm_bu)
testDispersion(sim_res_comm_bu)

# Poisson version of the Bottom-Up model with target variables
poisson_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                  z.X300_MF + z.X300_TSPG + z.X300_BAR + 
                  z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_winter, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_bu_tgt <- deviance(poisson_comm_bu_tgt) / df.residual(poisson_comm_bu_tgt)
dispersion_ratio_bu_tgt

sim_res_bu_tgt <- simulateResiduals(fittedModel = poisson_comm_bu_tgt)
testDispersion(sim_res_bu_tgt)
```

Top Down
```{r}
# Poisson version of the Top-Down model without target variables
poisson_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_winter, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td <- deviance(poisson_comm_td) / df.residual(poisson_comm_td)
dispersion_ratio_td

sim_res_td <- simulateResiduals(fittedModel = poisson_comm_td)
testDispersion(sim_res_td)

# Poisson version of the Top-Down model with target variables
poisson_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_winter, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td_tgt <- deviance(poisson_comm_td_tgt) / df.residual(poisson_comm_td_tgt)
dispersion_ratio_td_tgt

sim_res_td_tgt <- simulateResiduals(fittedModel = poisson_comm_td_tgt)
testDispersion(sim_res_td_tgt)

```

Apparent Competition
```{r}
# Poisson version of the Apparent Competition model without target variables
poisson_comm_app <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_winter, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app <- deviance(poisson_comm_app) / df.residual(poisson_comm_app)
dispersion_ratio_app

sim_res_app <- simulateResiduals(fittedModel = poisson_comm_app)
testDispersion(sim_res_app)

# Poisson version of the Apparent Competition model with target variables
poisson_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_winter, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app_tgt <- deviance(poisson_comm_app_tgt) / df.residual(poisson_comm_app_tgt)
dispersion_ratio_app_tgt

sim_res_app_tgt <- simulateResiduals(fittedModel = poisson_comm_app_tgt)
testDispersion(sim_res_app_tgt)

```

#### Poisson Model Selection
```{r}
model.sel(poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt)
```

################################################################################


## Model Selection
```{r}
model.sel(poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt, glmm_wk_cbou_wtr_null, glmm_wk_cbou_wtr_tgt_h, glmm_wk_cbou_wtr_tgt_l, glmm_wk_cbou_wtr_comm_bu, glmm_wk_cbou_wtr_comm_td, glmm_wk_cbou_wtr_comm_app, glmm_wk_cbou_wtr_comm_bu_tgt, glmm_wk_cbou_wtr_comm_td_tgt, glmm_wk_cbou_wtr_comm_app_tgt, glmm_wk_cbou_wtr_comm_app_2, glmm_wk_cbou_wtr_comm_app_2_tgt, glmm_wk_cbou_wtr_comm_app_3, glmm_wk_cbou_wtr_comm_app_3_tgt)
```

###Save Model Selection
```{r}
# Capture the model selection
#summary_output <- capture.output(model.sel(glmm_wk_cbou_wtr_null, glmm_wk_cbou_wtr_comm_bu, glmm_wk_cbou_wtr_comm_td, glmm_wk_cbou_wtr_comm_bu_tgt, glmm_wk_cbou_wtr_comm_td_tgt, glmm_wk_cbou_wtr_comm_app_2, glmm_wk_cbou_wtr_comm_app_2_tgt, glmm_wk_cbou_wtr_comm_app_3, glmm_wk_cbou_wtr_comm_app_3_tgt))

# Save the model selection to a CSV file
#write.csv(summary_output, file = "Tables/local_wtr_models_fnl.csv", row.names = FALSE)
```

###Save Top Model
```{r}
# Capture the summary output
#summary_output <- capture.output(summary(glmm_wk_cbou_wtr_comm_app_3))

# Save the summary data to a CSV file
#write.csv(summary_output, file = "Tables/local_wtr_comm_app_3.csv", row.names = FALSE)
```


############################################################################################################################################################################################################################

# 10. Local, Spring, WEEKLY detection data
```{r}
# Create a new data frame for winter
mod_dat_wk_cbou_spri <- read.csv("Processed_Data/glmm_wk_local_spr.csv", header=T)

#reorder factor levels for categorical variables
mod_dat_wk_cbou_spri$target_cons <- fct_relevel(mod_dat_wk_cbou_spri$target_cons, "None")
mod_dat_wk_cbou_spri$target_hydro <- fct_relevel(mod_dat_wk_cbou_spri$target_hydro, "None")
mod_dat_wk_cbou_spri$target_linear <- fct_relevel(mod_dat_wk_cbou_spri$target_linear, "None")

#check levels
levels(mod_dat_wk_cbou_spri$target_cons)
levels(mod_dat_wk_cbou_spri$target_hydro)
levels(mod_dat_wk_cbou_spri$target_linear)
```

##Simple Models
```{r}
#null model
glmm_wk_cbou_spri_null <- glmmTMB(Caribou ~ 
                     offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_spri_null)

#week model
glmm_wk_cbou_spri_wk <- glmmTMB(Caribou ~ 
                     week + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_spri_wk)
```

## Target
```{r}
glmm_wk_cbou_spri_tgt <- glmmTMB(Caribou ~ 
                     target_cons + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_spri, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_cbou_spri_tgt)

glmm_wk_cbou_spri_tgt_h <- glmmTMB(Caribou ~ 
                     target_hydro + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_spri, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_cbou_spri_tgt_h)

glmm_wk_cbou_spri_tgt_l <- glmmTMB(Caribou ~ 
                     target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_spri, family="nbinom2", control=glmmTMBControl(parallel=5))


summary(glmm_wk_cbou_spri_tgt_l)
```

## Committee Models

#### Bottom Up
wo tgt
```{r}
glmm_wk_cbou_spr_comm_bu <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_spr_comm_bu)
```

w tgt
```{r}
glmm_wk_cbou_spr_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + z.X300_MF + z.X300_TSPG + z.X300_BAR + z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_spr_comm_bu_tgt)
```

#### Top Down
wo tgt
```{r}
glmm_wk_cbou_spr_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_spr_comm_td)
```

w tgt
```{r}
glmm_wk_cbou_spr_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) + scale(Grizzly.Bear) + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_spr_comm_td_tgt)
```

####Apparent Competition
wo tgt
```{r}
glmm_wk_cbou_spr_comm_app <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + Muskox*Gray.Wolf + Moose*Grizzly.Bear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_spr_comm_app)
```

w tgt
```{r}
glmm_wk_cbou_spr_comm_app_tgt <- glmmTMB(Caribou ~ 
                 scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + Muskox*Gray.Wolf + Muskox*Grizzly.Bear + Moose*Gray.Wolf + Moose*Grizzly.Bear + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_spr_comm_app_tgt)
```

#####Simplified App Comp
two sets of different simplified models to try to solve convergence issues suggested by committee.

Species Only. Species detections scaled within model formula.
######NOTE: This results in model outputs exactly the same as the unscaled ung+pred model...

wout tgt
```{r}
glmm_wk_cbou_spr_comm_app_2 <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_spr_comm_app_2)
```

w tgt
```{r}
glmm_wk_cbou_spr_comm_app_2_tgt <- glmmTMB(Caribou ~ 
                  scale(Muskox) + scale(Moose) + scale(Gray.Wolf) + scale(Grizzly.Bear) + target_hydro + target_linear + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_spr_comm_app_2_tgt)
```

Consolidated and scaled Ungulates (moose+muskox) and Predators (Wolves+Griz) and an interaction term for Ung*Pred

wout tgt
```{r}
glmm_wk_cbou_spr_comm_app_3 <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + (1|location_site) , data=mod_dat_wk_cbou_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_spr_comm_app_3)
```

w tgt
```{r}
glmm_wk_cbou_spr_comm_app_3_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + offset(log(n_days_effort)) + target_hydro + target_linear + (1|location_site) , data=mod_dat_wk_cbou_spri, family="nbinom2", control=glmmTMBControl(parallel=5))

summary(glmm_wk_cbou_spr_comm_app_3_tgt)
```

####Committee Model Selection
```{r}
model.sel(glmm_wk_cbou_spri_null, glmm_wk_cbou_spr_comm_bu, glmm_wk_cbou_spr_comm_td, glmm_wk_cbou_spr_comm_bu_tgt, glmm_wk_cbou_spr_comm_td_tgt, glmm_wk_cbou_spr_comm_app_2, glmm_wk_cbou_spr_comm_app_2_tgt, glmm_wk_cbou_spr_comm_app_3, glmm_wk_cbou_spr_comm_app_3_tgt)
```

###################################################################################

###Over-dispersion Testing

Null Model
```{r}
# Poisson version of the random effects model
poisson_random_eff <- glmmTMB(Caribou ~ 1 + offset(log(n_days_effort)) + (1 | location_site), 
                              data = mod_dat_wk_cbou_spri, 
                              family = "poisson")

# Dispersion ratio
dispersion_ratio <- deviance(poisson_random_eff) / df.residual(poisson_random_eff)
dispersion_ratio  # >1.5 suggests overdispersion

# DHARMa check
library(DHARMa)
sim_res <- simulateResiduals(fittedModel = poisson_random_eff)
testDispersion(sim_res)
```

Bottom Up
```{r}
# Poisson version of the Bottom-Up model
poisson_comm_bu <- glmmTMB(Caribou ~ z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                           z.X300_MF + z.X300_TSPG + z.X300_BAR + 
                           offset(log(n_days_effort)) + (1 | location_site), 
                           data = mod_dat_wk_cbou_spri, 
                           family = "poisson")

# Dispersion ratio
dispersion_ratio_comm_bu <- deviance(poisson_comm_bu) / df.residual(poisson_comm_bu)
dispersion_ratio_comm_bu

# DHARMa check
sim_res_comm_bu <- simulateResiduals(fittedModel = poisson_comm_bu)
testDispersion(sim_res_comm_bu)

# Poisson version of the Bottom-Up model with target variables
poisson_comm_bu_tgt <- glmmTMB(Caribou ~ 
                  z.X300_SPPGLM + z.X300_TSPNF + z.X300_WET + z.X300_WAT + 
                  z.X300_MF + z.X300_TSPG + z.X300_BAR + 
                  z.mean_elev_300 + z.mean_tri_300 + z.esker_dist_m + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_spri, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_bu_tgt <- deviance(poisson_comm_bu_tgt) / df.residual(poisson_comm_bu_tgt)
dispersion_ratio_bu_tgt

sim_res_bu_tgt <- simulateResiduals(fittedModel = poisson_comm_bu_tgt)
testDispersion(sim_res_bu_tgt)
```

Top Down
```{r}
# Poisson version of the Top-Down model without target variables
poisson_comm_td <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_spri, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td <- deviance(poisson_comm_td) / df.residual(poisson_comm_td)
dispersion_ratio_td

sim_res_td <- simulateResiduals(fittedModel = poisson_comm_td)
testDispersion(sim_res_td)

# Poisson version of the Top-Down model with target variables
poisson_comm_td_tgt <- glmmTMB(Caribou ~ 
                  scale(Gray.Wolf) +  
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_spri, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_td_tgt <- deviance(poisson_comm_td_tgt) / df.residual(poisson_comm_td_tgt)
dispersion_ratio_td_tgt

sim_res_td_tgt <- simulateResiduals(fittedModel = poisson_comm_td_tgt)
testDispersion(sim_res_td_tgt)

```

Apparent Competition
```{r}
# Poisson version of the Apparent Competition model without target variables
poisson_comm_app <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_spri, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app <- deviance(poisson_comm_app) / df.residual(poisson_comm_app)
dispersion_ratio_app

sim_res_app <- simulateResiduals(fittedModel = poisson_comm_app)
testDispersion(sim_res_app)

# Poisson version of the Apparent Competition model with target variables
poisson_comm_app_tgt <- glmmTMB(Caribou ~ 
                  scale(Ungulates) + scale(Predators) + Ungulates*Predators + 
                  target_hydro + target_linear + 
                  offset(log(n_days_effort)) + (1 | location_site), 
                  data = mod_dat_wk_cbou_spri, 
                  family = "poisson")

# Check for overdispersion
dispersion_ratio_app_tgt <- deviance(poisson_comm_app_tgt) / df.residual(poisson_comm_app_tgt)
dispersion_ratio_app_tgt

sim_res_app_tgt <- simulateResiduals(fittedModel = poisson_comm_app_tgt)
testDispersion(sim_res_app_tgt)

```

#### Poisson Model Selection
```{r}
model.sel(poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt)
```

################################################################################


## Model Selection
```{r}
model.sel(glmm_wk_cbou_spri_null, glmm_wk_cbou_spr_comm_bu, glmm_wk_cbou_spr_comm_td, glmm_wk_cbou_spr_comm_bu_tgt, glmm_wk_cbou_spr_comm_td_tgt, glmm_wk_cbou_spr_comm_app_2, glmm_wk_cbou_spr_comm_app_2_tgt, glmm_wk_cbou_spr_comm_app_3, glmm_wk_cbou_spr_comm_app_3_tgt, poisson_random_eff, poisson_comm_bu, poisson_comm_td, poisson_comm_app, poisson_comm_bu_tgt, poisson_comm_td_tgt, poisson_comm_app_tgt)
```

###Save Model Selection
```{r}
# Capture the model selection
#summary_output <- capture.output(model.sel(glmm_wk_cbou_spri_null, glmm_wk_cbou_spr_comm_bu, glmm_wk_cbou_spr_comm_td, glmm_wk_cbou_spr_comm_bu_tgt, glmm_wk_cbou_spr_comm_td_tgt, glmm_wk_cbou_spr_comm_app_2, glmm_wk_cbou_spr_comm_app_3, glmm_wk_cbou_spr_comm_app_3_tgt))

# Save the model selection to a CSV file
#write.csv(summary_output, file = "Tables/local_spr_models_fnl.csv", row.names = FALSE)
```

###Save Top Model
```{r}
# Capture the summary output
#summary_output <- capture.output(summary(glmm_wk_cbou_spri_lcc_2))

# Save the summary data to a CSV file
#write.csv(summary_output, file = "Tables/local_spri_lcc_2.csv", row.names = FALSE)
```

#############################################################################################################################################################################################################################################

Some simple summary statistics to include in early parts of the results section. 

#11. Proportion of cameras detected

```{r}
#cluster analysis
tdn_clust_summaries_full<-read.csv("Processed_Data/wildRtrax/TDN_cam_summaries_full.csv")

# Specify the dataframe and species columns, excluding the first four columns
df <- tdn_clust_summaries_full
species_columns <- colnames(df)[3:72]  # Exclude the first columns

# Count the number of sampling sites where each species was detected
species_detected_sites <- colSums(df[, species_columns] > 0)

# Calculate the total number of sampling sites
total_sites <- count(unique(mod_dat_wk$location))

# Calculate the proportion of sampling sites each species was detected at
species_proportions <- species_detected_sites / total_sites

# Create a dataframe with species names and their respective proportions
summary_df <- data.frame(Species = names(species_proportions), Proportion_Detected = species_proportions)

# Print the new summary dataframe
print(summary_df)
```

#12. Species co-occurrences

##Regional, Multi-season
```{r}
# Select only the species detection columns by explicitly naming them
co_occurrences <- mod_dat_wk %>%
  dplyr::select(Caribou, Moose, Muskox, Gray.Wolf, Grizzly.Bear, Predators, Ungulates) %>%
  mutate(across(everything(), ~ . >= 1))

# Function to count co-occurrences for each species pair
count_co_occurrences <- function(df, species1, species2) {
  sum(df[[species1]] & df[[species2]])
}

# Get all unique species pairs
species <- c("Caribou", "Moose", "Muskox", "Gray.Wolf", "Grizzly.Bear", "Predators", "Ungulates")
pairs <- combn(species, 2, simplify = FALSE)

# Calculate co-occurrences for each pair
co_occurrence_counts <- sapply(pairs, function(pair) {
  count_co_occurrences(co_occurrences, pair[1], pair[2])
})

# Format the results into a readable data frame
results <- data.frame(
  Species1 = sapply(pairs, `[`, 1),
  Species2 = sapply(pairs, `[`, 2),
  Co_Occurrences = co_occurrence_counts
)

# View the results
print(results)
```

##Local, Multi-season
```{r}
# Select only the species detection columns by explicitly naming them
co_occurrences <- mod_dat_wk_cbou %>%
  dplyr::select(Caribou, Moose, Muskox, Gray.Wolf, Grizzly.Bear, Predators, Ungulates) %>%
  mutate(across(everything(), ~ . >= 1))

# Function to count co-occurrences for each species pair
count_co_occurrences <- function(df, species1, species2) {
  sum(df[[species1]] & df[[species2]])
}

# Get all unique species pairs
species <- c("Caribou", "Moose", "Muskox", "Gray.Wolf", "Grizzly.Bear", "Predators", "Ungulates")
pairs <- combn(species, 2, simplify = FALSE)

# Calculate co-occurrences for each pair
co_occurrence_counts <- sapply(pairs, function(pair) {
  count_co_occurrences(co_occurrences, pair[1], pair[2])
})

# Format the results into a readable data frame
results <- data.frame(
  Species1 = sapply(pairs, `[`, 1),
  Species2 = sapply(pairs, `[`, 2),
  Co_Occurrences = co_occurrence_counts
)

# View the results
print(results)
```

##Local, Summer
```{r}
# Select only the species detection columns by explicitly naming them
co_occurrences <- mod_dat_wk_cbou_summer %>%
  dplyr::select(Caribou, Moose, Muskox, Gray.Wolf, Grizzly.Bear, Predators, Ungulates) %>%
  mutate(across(everything(), ~ . >= 1))

# Function to count co-occurrences for each species pair
count_co_occurrences <- function(df, species1, species2) {
  sum(df[[species1]] & df[[species2]])
}

# Get all unique species pairs
species <- c("Caribou", "Moose", "Muskox", "Gray.Wolf", "Grizzly.Bear", "Predators", "Ungulates")
pairs <- combn(species, 2, simplify = FALSE)

# Calculate co-occurrences for each pair
co_occurrence_counts <- sapply(pairs, function(pair) {
  count_co_occurrences(co_occurrences, pair[1], pair[2])
})

# Format the results into a readable data frame
results <- data.frame(
  Species1 = sapply(pairs, `[`, 1),
  Species2 = sapply(pairs, `[`, 2),
  Co_Occurrences = co_occurrence_counts
)

# View the results
print(results)
```

##Local, Fall
```{r}
# Select only the species detection columns by explicitly naming them
co_occurrences <- mod_dat_wk_cbou_fall %>%
  dplyr::select(Caribou, Moose, Muskox, Gray.Wolf, Grizzly.Bear, Predators, Ungulates) %>%
  mutate(across(everything(), ~ . >= 1))

# Function to count co-occurrences for each species pair
count_co_occurrences <- function(df, species1, species2) {
  sum(df[[species1]] & df[[species2]])
}

# Get all unique species pairs
species <- c("Caribou", "Moose", "Muskox", "Gray.Wolf", "Grizzly.Bear", "Predators", "Ungulates")
pairs <- combn(species, 2, simplify = FALSE)

# Calculate co-occurrences for each pair
co_occurrence_counts <- sapply(pairs, function(pair) {
  count_co_occurrences(co_occurrences, pair[1], pair[2])
})

# Format the results into a readable data frame
results <- data.frame(
  Species1 = sapply(pairs, `[`, 1),
  Species2 = sapply(pairs, `[`, 2),
  Co_Occurrences = co_occurrence_counts
)

# View the results
print(results)
```


##Local, Winter

no predator:ungulate or caribou:ungulate in the local, winter. Caribou:Wolf/ caribou:predator n=4. 
```{r}
# Select only the species detection columns by explicitly naming them
co_occurrences <- mod_dat_wk_cbou_winter %>%
  dplyr::select(Caribou, Moose, Muskox, Gray.Wolf, Grizzly.Bear, Predators, Ungulates) %>%
  mutate(across(everything(), ~ . >= 1))

# Function to count co-occurrences for each species pair
count_co_occurrences <- function(df, species1, species2) {
  sum(df[[species1]] & df[[species2]])
}

# Get all unique species pairs
species <- c("Caribou", "Moose", "Muskox", "Gray.Wolf", "Grizzly.Bear", "Predators", "Ungulates")
pairs <- combn(species, 2, simplify = FALSE)

# Calculate co-occurrences for each pair
co_occurrence_counts <- sapply(pairs, function(pair) {
  count_co_occurrences(co_occurrences, pair[1], pair[2])
})

# Format the results into a readable data frame
results <- data.frame(
  Species1 = sapply(pairs, `[`, 1),
  Species2 = sapply(pairs, `[`, 2),
  Co_Occurrences = co_occurrence_counts
)

# View the results
print(results)
```

##Local, Spring

no caribou:ungulate or caribou:predator in the local spring. n=3 predator:ungulate, muskox:wolf =2, moose:grizzly = 1 
```{r}
# Select only the species detection columns by explicitly naming them
co_occurrences <- mod_dat_wk_cbou_spri %>%
  dplyr::select(Caribou, Moose, Muskox, Gray.Wolf, Grizzly.Bear, Predators, Ungulates) %>%
  mutate(across(everything(), ~ . >= 1))

# Function to count co-occurrences for each species pair
count_co_occurrences <- function(df, species1, species2) {
  sum(df[[species1]] & df[[species2]])
}

# Get all unique species pairs
species <- c("Caribou", "Moose", "Muskox", "Gray.Wolf", "Grizzly.Bear", "Predators", "Ungulates")
pairs <- combn(species, 2, simplify = FALSE)

# Calculate co-occurrences for each pair
co_occurrence_counts <- sapply(pairs, function(pair) {
  count_co_occurrences(co_occurrences, pair[1], pair[2])
})

# Format the results into a readable data frame
results <- data.frame(
  Species1 = sapply(pairs, `[`, 1),
  Species2 = sapply(pairs, `[`, 2),
  Co_Occurrences = co_occurrence_counts
)

# View the results
print(results)
```

#13. Targets by species

looking at targets and species for the local/spring extent since that's where we got convergence issues in species/target models (but not bottom up target)

```{r}
# Count occurrences for target_linear
species_linear_counts <- mod_dat_wk_cbou_spri %>%
  # Filter rows where species have at least one detection
  filter(Caribou >= 1 | Moose >= 1 | Muskox >= 1 | Gray.Wolf >= 1 | Grizzly.Bear >= 1) %>%
  # Pivot the data longer to analyze each species individually
  pivot_longer(cols = c(Caribou, Moose, Muskox, Gray.Wolf, Grizzly.Bear), 
               names_to = "Species", 
               values_to = "Detections") %>%
  # Keep rows where species detections are greater than or equal to 1
  filter(Detections >= 1) %>%
  # Group by species and target_linear
  group_by(Species, target_linear) %>%
  # Count the number of occurrences for each combination
  summarise(Count = n(), .groups = 'drop')

# View the results for target_linear
print(species_linear_counts)

# Count occurrences for target_hydro
species_hydro_counts <- mod_dat_wk %>%
  # Filter rows where species have at least one detection
  filter(Caribou >= 1 | Moose >= 1 | Muskox >= 1 | Gray.Wolf >= 1 | Grizzly.Bear >= 1) %>%
  # Pivot the data longer to analyze each species individually
  pivot_longer(cols = c(Caribou, Moose, Muskox, Gray.Wolf, Grizzly.Bear), 
               names_to = "Species", 
               values_to = "Detections") %>%
  # Keep rows where species detections are greater than or equal to 1
  filter(Detections >= 1) %>%
  # Group by species and target_hydro
  group_by(Species, target_hydro) %>%
  # Count the number of occurrences for each combination
  summarise(Count = n(), .groups = 'drop')

# View the results for target_hydro
print(species_hydro_counts)
```


