---
title: "9e_wolf_coatcolour_analysis"
output: html_document
date: "2024-09-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r}
# Check you have them and load them
list.of.packages <- c("kableExtra", "tidyr", "ggplot2", "gridExtra", "dplyr", "Hmsc", "jtools", "lubridate", "corrplot", "MuMIn","stringr","sf","raster","leaflet", "tidyverse","htmlwidgets","webshot", "purrr", "magick","forcats","multcomp", "reshape2", "lme4", "tidyr", "stats")

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
lapply(list.of.packages, require, character.only = TRUE)
```

#  Prepare Location Data

```{r}
locs <- read.csv("Processed_Data/TDN_camera_locations_and_covariates_cleaned.csv", header=T)

# Convert to categorical factors
locs <- locs %>% 
            mutate_if(is.character,as.factor)

# You should also standardize your covariates - it helps models coverage and facillitates comparison of effects sizes

#NEED TO RUN THIS SO LAT/LONG DONT GET STANDARDIZED
#non response variable species should be scaled but that can manually be done in the GLMM formulas
library(MuMIn)
z_locs <- stdize(locs, omit.cols = c("latitude","longitude","latitude_site","longitude_site","spatial_scale"))
```

#Prepare Wolf Data

```{r}
wolf_indv <- read.csv("Processed_Data/wolf_coatcolour_individuals.csv", header=T)

# Perform the left join based on the 'location' column
wolf_indv_with_covariates <- wolf_indv %>%
  left_join(z_locs, by = "location")

# View the first few rows of the resulting data frame to verify the join
head(wolf_indv_with_covariates)
```

# Summarize Data by Location
```{r}
# Step 1: Count occurrences of each coat_colour per location
counted_df <- wolf_indv_with_covariates %>%
  group_by(location, coat_colour) %>%
  summarise(count = n(), .groups = 'drop')

# Step 2: Pivot to wide format with separate columns for each coat_colour
pivot_df <- counted_df %>%
  pivot_wider(names_from = coat_colour, values_from = count, values_fill = 0)

# Step 3: Remove the 'day', 'comment', and 'coat_colour' columns and keep distinct rows for each location
wolf_indv_cleaned <- wolf_indv_with_covariates %>%
  dplyr::select(-day, -comment, -coat_colour) %>% # Remove unnecessary columns
  distinct(location, .keep_all = TRUE) # Keep one row per location

# Step 4: Join the pivoted data with the cleaned data frame to keep covariates
summary_with_covariates <- wolf_indv_cleaned %>%
  left_join(pivot_df, by = "location")

# Step 5: Reorder columns to place Dark, Light, and Unknown as 2nd, 3rd, and 4th columns
summary_with_covariates <- summary_with_covariates %>%
  dplyr::select(location, Dark, Light, Unknown, everything())

# View the final result
print(summary_with_covariates)
```

#Summarize Data by Cluster
```{r}
# Step 1: Group by location_site and summarize the total counts
summary_location_site <- summary_with_covariates %>%
  group_by(location_site) %>%
  summarise(
    total_Dark = sum(Dark, na.rm = TRUE),
    total_Light = sum(Light, na.rm = TRUE),
    total_Unknown = sum(Unknown, na.rm = TRUE),
    latitude_site = first(latitude_site), # Assuming latitude_site is the same for all locations within a location_site
    longitude_site = first(longitude_site) # Assuming longitude_site is the same for all locations within a location_site
  )

# View the new summarized data frame
print(summary_location_site)
```

#Summarize Data by Spatial Extent
```{r}
# Summarize the counts of Dark, Light, and Unknown by spatial_scale
summary_spatial_scale <- summary_with_covariates %>%
  group_by(spatial_scale) %>%
  summarise(
    total_Dark = sum(Dark, na.rm = TRUE),
    total_Light = sum(Light, na.rm = TRUE),
    total_Unknown = sum(Unknown, na.rm = TRUE)
  )

# View the new summarized data frame
print(summary_spatial_scale)
```

#Summarize Data by Season

Add caribou-centric seasons
```{r}
# Let's create a new column for the four seasons based on the specified date ranges
wolf_indv_with_covariates$four_season <- "Summer"
wolf_indv_with_covariates$four_season[wolf_indv_with_covariates$day >= as.Date("2021-07-29") & wolf_indv_with_covariates$day <= as.Date("2021-10-20")] <- "Summer"
wolf_indv_with_covariates$four_season[wolf_indv_with_covariates$day >= as.Date("2021-10-21") & wolf_indv_with_covariates$day <= as.Date("2021-12-14")] <- "Fall"
wolf_indv_with_covariates$four_season[wolf_indv_with_covariates$day >= as.Date("2021-12-15") & wolf_indv_with_covariates$day <= as.Date("2022-04-04")] <- "Winter"
wolf_indv_with_covariates$four_season[wolf_indv_with_covariates$day >= as.Date("2022-04-05") & wolf_indv_with_covariates$day <= as.Date("2022-06-21")] <- "Spring"
wolf_indv_with_covariates$four_season[wolf_indv_with_covariates$day >= as.Date("2022-06-22") & wolf_indv_with_covariates$day <= as.Date("2022-08-24")] <- "Summer"

# Get the column names
column_names <- names(wolf_indv_with_covariates)

# Reorder the columns
new_column_order <- c(column_names[1:3], "four_season", column_names[4:length(column_names)])

# Create the reordered data frame
wolf_indv_with_covariates <- wolf_indv_with_covariates[, new_column_order]

# Make it a factor
wolf_indv_with_covariates <- wolf_indv_with_covariates %>% 
            mutate_if(is.character, as.factor)
```

seasonal/spatial analysis
```{r}
# Step 1: Summarize by spatial_scale and four_season
summary_spatial_scale_season <- wolf_indv_with_covariates %>%
  group_by(spatial_scale, four_season, coat_colour) %>%
  summarise(count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = coat_colour, values_from = count, values_fill = 0)

# Step 2: Summarize by four_season alone (regardless of spatial_scale)
summary_season <- wolf_indv_with_covariates %>%
  group_by(four_season, coat_colour) %>%
  summarise(count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = coat_colour, values_from = count, values_fill = 0) %>%
  mutate(spatial_scale = "Overall")  # Add a column to indicate this is the overall summary
```

#Repeat after removing outlier

Remove wolf den camera at BIO-TDN-032-05
```{r}
# Remove observations from location BIO-TDN-032-05
filtered_wolf_indv <- wolf_indv_with_covariates %>%
  filter(location != "BIO-TDN-032-05")
```

```{r}
# Summarize by location_site and include latitude_site and longitude_site
summary_location_site_no_outlier <- filtered_wolf_indv %>%
  group_by(location_site, latitude_site, longitude_site) %>%
  summarise(
    Dark = sum(coat_colour == "Dark", na.rm = TRUE),
    Light = sum(coat_colour == "Light", na.rm = TRUE),
    Unknown = sum(coat_colour == "Unknown", na.rm = TRUE)
  )
```

by spatial extent
```{r}
# Summarize by spatial_scale without outlier
summary_spatial_scale_no_outlier <- filtered_wolf_indv %>%
  group_by(spatial_scale) %>%
  summarise(
    Dark = sum(coat_colour == "Dark", na.rm = TRUE),
    Light = sum(coat_colour == "Light", na.rm = TRUE),
    Unknown = sum(coat_colour == "Unknown", na.rm = TRUE)
  )

```

by season
```{r}
# Summarize by four_season without outlier
summary_four_season_no_outlier <- filtered_wolf_indv %>%
  group_by(four_season) %>%
  summarise(
    Dark = sum(coat_colour == "Dark", na.rm = TRUE),
    Light = sum(coat_colour == "Light", na.rm = TRUE),
    Unknown = sum(coat_colour == "Unknown", na.rm = TRUE)
  )
```

by time/space
```{r}
# Summarize by spatial_scale and four_season without outlier
summary_spatial_scale_season_no_outlier <- filtered_wolf_indv %>%
  group_by(spatial_scale, four_season) %>%
  summarise(
    Dark = sum(coat_colour == "Dark", na.rm = TRUE),
    Light = sum(coat_colour == "Light", na.rm = TRUE),
    Unknown = sum(coat_colour == "Unknown", na.rm = TRUE)
  )

```


#Correlation analysis

Note: Don't take correlation coefficients between landcovers seriously because this df only includes locations where wolves were detected.

Light + SPPGLM (0.32)
Dark + elev (-0.47)
Dark + TSPS (0.41)
Dark + TSPBDF (0.53)
```{r}

# First we need to create a correlation matrix between the different variables of interest
Q <- cor(summary_with_covariates[, c("z.X300_TSPNF", "z.X300_WET", "z.X300_WAT", "z.X300_SPTNF", "z.X300_MF", "z.X300_TSPG", "z.X300_TSPS", "z.X300_SPPSLM", "z.X300_SPPGLM", "z.X300_BAR", "z.X300_TSPBDF", "z.mean_cc", "z.esker_dist_m","z.mean_elev_300", "z.mean_tri_300", "z.treeline_distance_m", "Dark", "Light", "Unknown")])

corrplot(Q)
```

pairwise correlations >0.7 exclude from model
```{r}
corrplot(Q,                              #The correlation matrix we made
         method="color",                 # How we want the cells 
         type="upper",                   # Just show the upper part (it is usually mirrored)
         order="hclust",                 # Order the variables using the hclust method
         addCoef.col = "black",          # Add coefficient of correlation  
         number.cex = .6,
         tl.col="black", tl.srt=45,      # Control the text label color and rotation
         diag=F                          # Suppress the diagonal correlations (which are 1 anyway)
         )
```

#Save CSVs
```{r}
# Save the final dataframe as a CSV file
write.csv(summary_with_covariates, file="Processed_Data/wolf_coat_summary.csv", row.names = FALSE)

write.csv(summary_location_site, file="Processed_Data/wolf_coat_summary_clusters.csv", row.names = FALSE)

write.csv(summary_spatial_scale_season, file="Processed_Data/wolf_coat_summary_scale_season.csv", row.names = FALSE)

#summaries without the outlier at BIO-TDN-032-05 (wolf den)

write.csv(summary_location_site_no_outlier, file="Processed_Data/wolf_coat_summary_clusters_nooutlier.csv", row.names = FALSE)

write.csv(summary_spatial_scale_season_no_outlier, file="Processed_Data/wolf_coat_summary_scale_season_nooutlier.csv", row.names = FALSE)
```

